---
title: "One_row_per_id"
output: html_notebook
---


# Libraries

```{r}
library(ggplot2)
library(hrbrthemes)
library(tidyverse)
library(plotly)
library(BBmisc)
library(scales)
library(dplyr)
library(naniar)
library(gridExtra)
library(knitr)
library(ggplot2)
library(hrbrthemes)
library(tidyverse)
library(plotly)
library(BBmisc)
library(scales)
library(dplyr)
library(naniar)
library(gridExtra)
library(knitr)
library(finalfit)
library(data.table)

```
# Global variables
```{r}
# MasterAnalysisOn==1 prevents the dateRange and readingwanted variables from
# being overwritten, but the option to turn this off and run this script without
# first running MasterAnalysis.R is available by setting MasterAnalysisOn==0 and then
# manually selecting the dateRange and readingwanted variables.
MasterAnalysisOn <- 0
if (MasterAnalysisOn==0) {
dateRange <- 5 # 1, 3 or 5 days
readingwanted <- 1 # 0-worst, 1-first, 2-mean
}
```


# Load in data files
## Outcome data

### NBT Outcomes

```{r}
NBT_outcomes <- read.csv(file("NBT_outcomes.csv"))
NBT_outcomes = NBT_outcomes %>% 
  rename(
    ID = uob_ID,
    admissionDate = admission_date,
    dischargeDate = discharge_date,
  )
NBT_outcomes$admissionDate = as.Date(NBT_outcomes$admissionDate, format="%d/%m/%Y")
NBT_outcomes$dischargeDate = as.Date(NBT_outcomes$dischargeDate, format="%d/%m/%Y")
NBT_outcomes_deaths = NBT_outcomes %>%
  filter(DischargeOutcomeDesc == "Patient Died")
NBT_outcomes_deaths$deathDate = NBT_outcomes_deaths$dischargeDate
NBT_outcomes <- merge(NBT_outcomes,NBT_outcomes_deaths,all=TRUE)
NBT_outcomes$ITU_Start = as.Date(NBT_outcomes$ITU_Start, format="%d/%m/%Y")
NBT_outcomes$ITU_End = as.Date(NBT_outcomes$ITU_End, format="%d/%m/%Y")
NBT_outcomes$Site = "NBT"
NBT_outcomes2 <- dplyr::select(NBT_outcomes,c(ID,admissionDate,dischargeDate,
                                       ITU_Start,ITU_End,deathDate,Site))
```

### UHB Outcomes

```{r}
UHB_outcomes1 <- read.csv(file("UHB_outcomes1.csv"))
UHB_outcomes1 = UHB_outcomes1 %>% 
  rename(
    ID = uob_ID,
    admissionDate = attend_date,
    deathDate = fu_death_date,
  )
UHB_outcomes1$admissionDate = as.Date(UHB_outcomes1$admissionDate, format="%d/%m/%Y")
UHB_outcomes1$dischargeDate = as.Date(UHB_outcomes1$admissionDate + as.integer(UHB_outcomes1$hospital_length_of_stay))
UHB_outcomes1$deathDate = as.Date(UHB_outcomes1$deathDate, format="%d/%m/%Y")
UHB_outcomes1$ITU_Start <- as.Date(NA)
UHB_outcomes1$ITU_End <- as.Date(NA)
UHB_outcomes1$Site = "UHB1"
UHB_outcomes12 = UHB_outcomes1 %>% dplyr::select(ID,admissionDate,dischargeDate,ITU_Start,ITU_End,deathDate,Site)

UHB_outcomes2 <- read.csv(file("UHB_outcomes2.csv"))
UHB_outcomes2 = UHB_outcomes2 %>% 
  rename(
    ID = uob_ID,
    admissionDate = attend_dte,
  )
UHB_outcomes2$admissionDate = as.Date(UHB_outcomes2$admissionDate, format="%d/%m/%Y")
UHB_outcomes2 = UHB_outcomes2 %>% 
  rename(
    dischargeDate = outcome_dte,
  )
UHB_outcomes2$dischargeDate = as.Date(UHB_outcomes2$dischargeDate, format="%d/%m/%Y")
UHB_outcomes2_deaths = UHB_outcomes2 %>%
  filter(outcome == 3)
UHB_outcomes2_deaths$deathDate = UHB_outcomes2_deaths$dischargeDate
UHB_outcomes2 <- merge(UHB_outcomes2,UHB_outcomes2_deaths,all=TRUE)
UHB_outcomes2$ITU_Start <- as.Date(NA)
UHB_outcomes2$ITU_End <- as.Date(NA)
UHB_outcomes2$Site = "UHB2"
UHB_outcomes22 = UHB_outcomes2 %>% dplyr::select(ID,admissionDate,dischargeDate,ITU_Start,ITU_End,deathDate,Site)
```

### Weston outcomes

```{r}
WestonOutcomes <- read.csv(file("Weston.Outcomes.csv"))
WestonOutcomes = WestonOutcomes %>% 
  rename(
    ID = uob_ID,
    admissionDate = Admission.date,
    dischargeDate = Discharge.date,
    ITU_Start = ICU.Admission.Date,
    ITU_End = ICU.Discharge.Date,
    deathDate = Date.of.Death,
  )
WestonOutcomes$admissionDate = as.Date(WestonOutcomes$admissionDate, format="%d/%m/%Y")
WestonOutcomes$dischargeDate = as.Date(WestonOutcomes$dischargeDate, format="%d/%m/%Y")
WestonOutcomes$ITU_Start = as.Date(WestonOutcomes$ITU_Start, format="%d/%m/%Y")
WestonOutcomes$ITU_End = as.Date(WestonOutcomes$ITU_End, format="%d/%m/%Y")
WestonOutcomes$deathDate = as.Date(WestonOutcomes$deathDate, format="%d/%m/%Y")
WestonOutcomes$Site = "Weston"
WestonOutcomes2 = WestonOutcomes %>% dplyr::select(ID,admissionDate,dischargeDate,ITU_Start,ITU_End,deathDate, Site)
```

#### Vir - Virology

```{r}
Vir <- read.csv(file("Vir.csv"))
Vir['Measure']='Vir'
Vir$Sample.Date = as.Date(Vir$Sample.Date, format="%d/%m/%Y")
Vir = Vir %>% 
  rename(
    ID = uob_ID,
    date = Sample.Date,
    Adenovirus = Adenovirus..PCR.,
    Human_Metapneumovirus = Human.metapneumovirus..PCR.,
    Influenza_A = Influenza.A..PCR.,
    Influenza_B = Influenza.B..PCR.,
    Parainfluenza_Type_1 = Parainfluenza.Type.1..PCR.,
    Parainfluenza_Type_2 = Parainfluenza.Type.2..PCR.,
    Parainfluenza_Type_3 = Parainfluenza.Type.3..PCR.,
    Parainfluenza_Type_4 = Parainfluenza.Type.4..PCR.,
    Respiratory_Syncytial_Virus = Respiratory.Syncytial.Virus..PCR.,
    Rhinovirus = Rhinovirus..PCR.,
  )
```

## Merge Outcome data

```{r}
# Merge outcomes data
totalOutcomes <- rbind(UHB_outcomes12,UHB_outcomes22,NBT_outcomes2,WestonOutcomes2) # NBT Outcomes must be excluded as inconsistent
totalOutcomes$deathDate = as.Date(totalOutcomes$deathDate, format="%d/%m/%Y")
totalOutcomes$ITU_Start = as.Date(totalOutcomes$ITU_Start, format="%d/%m/%Y")
totalOutcomes$ITU_End = as.Date(totalOutcomes$ITU_End, format="%d/%m/%Y")
totalOutcomes$dischargeDate = as.Date(totalOutcomes$dischargeDate, format="%d/%m/%Y")
```


## Demographics Table
Age and gender for every individual

```{r}
dem <- read.csv(file("masterlist.csv"))
dem <- dem %>%
  rename(ID = uob_ID, Age = agecat) %>%
  distinct(ID, .keep_all = TRUE) %>%
  dplyr::select(ID,Gender,Age)
```

## Merge outcomes with demographics

```{r}
total = merge(totalOutcomes,dem, by="ID")
```

## Remove those without outcome info
```{r}
# Remove those without admission information
total <- total %>% filter(!is.na(admissionDate))
```

# Missing discharge info
```{r}
# Remove those without discharge information
total <- total %>% filter(!is.na(dischargeDate))
```

# Age less than 18
```{r}
# Remove those less than 18
total <- total %>% filter(Age >= 18)
```

### Those that have died
```{r}
deceasedSubset = subset(total, !is.na(total$deathDate))
deceasedSubset$died = TRUE
```

### Add new column for died / didn't die to total
```{r}
total = merge(total,deceasedSubset, all.x=TRUE)
total$died[is.na(total$died)] <- FALSE

```

### Those that went to ICU
```{r}
ICU_subset = subset(totalOutcomes, !is.na(totalOutcomes$ITU_Start))
ICU_subset$went_to_icu = TRUE

```


### Add new column for went to ICU / didn't go to ICU
```{r}
total = merge(total,ICU_subset, all.x=TRUE)
total$went_to_icu[is.na(total$went_to_icu)] <- FALSE
```


### Died or went to ICU
```{r}
total$severeOutcome[total$went_to_icu == TRUE | total$died == TRUE] <- TRUE
total$severeOutcome[is.na(total$severeOutcome)] <- FALSE
```

## Add FIRST covid-positive date
- Find first covid-positive test and add as new column
- dplyr::select only ID and positive date
- Remove duplicates
- Add to total outcomes
```{r}
CovidCT <- read.csv(file("CovidCT.csv"))
CovidCT['Measure']='CovidCT'
CovidCT$Specimen.Date = as.Date(CovidCT$Specimen.Date, format="%d/%m/%Y")
CovidCT = CovidCT %>% 
  rename(
     ID = uob_ID,
    date = Specimen.Date,
  )

uniqueIDs = unique(CovidCT$ID)
CovidCT['positiveDate'] <- as.Date(NA)


for (i in uniqueIDs){
  for (j in length(CovidCT$date[CovidCT$ID == i])){
      CovidCT[CovidCT$ID == i,]$positiveDate <- as.Date(CovidCT[CovidCT$ID == i,]$date[1], format="%d%m%Y")
  }
}

CovidCT <- CovidCT %>% dplyr::select(ID,positiveDate) %>% distinct()

total <- left_join(total,CovidCT)

```
# Number of people who have multiple admissions

```{r}
duplicates <- setDT(totalOutcomes)[, .N, ID]
for (i in (1:10)){
  print(i)
  print(nrow(duplicates[N==i]))
}

total <- merge(total,duplicates, by="ID")

```

# Only keep first admission
```{r}
for (id in unique(total$ID)){
  total[total$ID==id,] <- total[total$ID==id,][1,]
}
total <- unique(total)
```


### Load variable data
#### BE - Bicarbonate Excess

```{r}
BE <- read.csv(file("BE.csv"))
BE$Date.Booked.In = as.Date(BE$Date.Booked.In, format="%d/%m/%Y")
BE = BE %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
BE = BE %>%
  rename(
    BE_val = Numeric.Result
  )

BE = BE %>% dplyr::select(ID,date,BE_val)

BE <- BE[complete.cases(BE),]

BE2 <- data.frame(ID=character(),
                  BE_val=character())

commonIDs <- intersect(total$ID,BE$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = BE[BE$ID==id,]$date
  # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = BE[BE$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$BE_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true
    # if either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 22 | highest > 29),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 22 | first > 29),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 22 | average > 29),"Abnormal","Normal")
    }
    BE2 <- BE2 %>% add_row(ID=id,BE_val=value)
  }
}

BE <- BE2
rm(BE2)
```

#### BNP - B-type natriuretic peptide

```{r}
BNP <- read.csv(file("BNP.csv"))
BNP$Date.Booked.In = as.Date(BNP$Date.Booked.In, format="%d/%m/%Y")
BNP = BNP %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
BNP = BNP %>%
  rename(
    BNP_val = Numeric.Result
  )

BNP = BNP %>% dplyr::select(ID,date,BNP_val)

BNP <- BNP[complete.cases(BNP),]

BNP2 <- data.frame(ID=character(),
                  BNP_val=character())

commonIDs <- intersect(total$ID,BNP$ID)

for (id in unique(commonIDs)){
  # Get all dates for this ID and variable
  idDates = BNP[BNP$ID==id,]$date
  # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id][1]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = BNP[BNP$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$BNP_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    age = total$Age[total$ID==id]
    gender = total$Gender[total$ID==id]

    if (age < 70){
      # Men under 70
      if (gender == "M") {
        if (highest >= 100){
          value = "Abnormal"
        } else {
          value = "Normal"
        }
      } else{
        # Women under 70
        if (highest >= 150){
          value = "Abnormal"
        } else {
          value = "Normal"
        }
      }
    } else {
      # All 70 and over
      if (highest >= 300){
        value = "Abnormal"
      } else {
        value = "Normal"
      }
    }
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    age = total$Age[total$ID==id]
    gender = total$Gender[total$ID==id]

    if (age < 70){
      # Men under 70
      if (gender == "M") {
        if (first >= 100){
          value = "Abnormal"
        } else {
          value = "Normal"
        }
      } else{
        # Women under 70
        if (first >= 150){
          value = "Abnormal"
        } else {
          value = "Normal"
        }
      }
    } else {
      # All 70 and over
      if (first >= 300){
        value = "Abnormal"
      } else {
        value = "Normal"
      }
    }
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      age = total$Age[total$ID==id]
    gender = total$Gender[total$ID==id]

    if (age < 70){
      # Men under 70
      if (gender == "M") {
        if (average >= 100){
          value = "Abnormal"
        } else {
          value = "Normal"
        }
      } else{
        # Women under 70
        if (average >= 150){
          value = "Abnormal"
        } else {
          value = "Normal"
        }
      }
    } else {
      # All 70 and over
      if (average >= 300){
        value = "Abnormal"
      } else {
        value = "Normal"
      }
    }
    }
    # Add this 
    BNP2 <- BNP2 %>% add_row(ID=id,BNP_val=value)
  }
}

BNP <- BNP2
rm(BNP2)

```

#### CRP - C-Reactive Protein

```{r}
CRP <- read.csv(file("CRP.csv"))
CRP$Date.Booked.In = as.Date(CRP$Date.Booked.In, format="%d/%m/%Y")
CRP = CRP %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
CRP = CRP %>%
  rename(
    CRP_val = Numeric.Result
  )

CRP = CRP %>% dplyr::select(ID,date,CRP_val)

CRP <- CRP[complete.cases(CRP),]

CRP2 <- data.frame(ID=character(),
                  CRP_val=character())

commonIDs <- intersect(total$ID,CRP$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = CRP[CRP$ID==id,]$date
  # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = CRP[CRP$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$CRP_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((highest >= 6),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first >= 6),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average >= 6),"Abnormal","Normal")
    }
    # Add this 
    CRP2 <- CRP2 %>% add_row(ID=id,CRP_val=value)
  }
}

CRP <- CRP2
rm(CRP2)

```


#### DDM - D-Dimer 

```{r}
DDM <- read.csv(file("DDM.csv"))
#DDM_N <- DDM %>% 
#  filter(str_detect(Source.PCG.Code,"N")) %>%
#  transmute(
#    uob_ID = uob_ID,
#    Date.Booked.In = Date.Booked.In,
#    Source.PCG.Code = Source.PCG.Code,
#    Result..Not.Large.= Result..Not.Large.,
#    Numeric.Result = as.double(Result..Not.Large.)*1000
#    )

# DDM$Numeric.Result[str_detect(DDM$Source.PCG.Code,"N")] <- DDM_N$Numeric.Result

DDM$Date.Booked.In = as.Date(DDM$Date.Booked.In, format="%d/%m/%Y")
DDM = DDM %>% 
  rename(
    ID = uob_ID,
    date = Date.Booked.In,
    DDM_val = Numeric.Result,
  )

DDM = DDM %>% dplyr::select(ID,date,DDM_val)

DDM <- DDM[complete.cases(DDM),]

DDM2 <- data.frame(ID=character(),
                  DDM_val=character())

commonIDs <- intersect(total$ID,DDM$ID)

for (id in unique(commonIDs)){
  # Get all dates for this ID and variable
  idDates = DDM[DDM$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id][1]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = DDM[DDM$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$DDM_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    age = total$Age[total$ID==id]
    
    if (age <= 60){
      value = ifelse(highest >= 500,"Abnormal","Normal")
    }else if(age > 60 & age <= 70){
      value = ifelse(highest >= 600,"Abnormal","Normal")
    }else if(age > 70 & age <= 80){
      value = ifelse(highest >= 700,"Abnormal","Normal")
    }else if(age > 80 & age <=90){
      value = ifelse(highest >= 800,"Abnormal","Normal")
    }else {
      value = ifelse(highest >= 900,"Abnormal","Normal")
    }
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    age = total$Age[total$ID==id]
    
    if (age <= 60){
      value = ifelse(first >= 500,"Abnormal","Normal")
    }else if(age > 60 & age <= 70){
      value = ifelse(first >= 600,"Abnormal","Normal")
    }else if(age > 70 & age <= 80){
      value = ifelse(first >= 700,"Abnormal","Normal")
    }else if(age > 80 & age <=90){
      value = ifelse(first >= 800,"Abnormal","Normal")
    }else {
      value = ifelse(first >= 900,"Abnormal","Normal")
    }
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      age = total$Age[total$ID==id]
    
    if (age <= 60){
      value = ifelse(average >= 500,"Abnormal","Normal")
    }else if(age > 60 & age <= 70){
      value = ifelse(average >= 600,"Abnormal","Normal")
    }else if(age > 70 & age <= 80){
      value = ifelse(average >= 700,"Abnormal","Normal")
    }else if(age > 80 & age <=90){
      value = ifelse(average >= 800,"Abnormal","Normal")
    }else {
      value = ifelse(average >= 900,"Abnormal","Normal")
    }
    }
    # Add this 
    DDM2 <- DDM2 %>% add_row(ID=id,DDM_val=value)
  }
}

DDM <- DDM2
rm(DDM2)

```

#### eGFR - Estimated Glomerular Filtration Rate

```{r}
eGFR <- read.csv(file("eGFR.csv"))
eGFR$Date.Booked.In = as.Date(eGFR$Date.Booked.In, format="%d/%m/%Y")
eGFR = eGFR %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
eGFR = eGFR %>%
  rename(
    eGFR_val = Numeric.Result
  )

eGFR$eGFR_val[eGFR$Result..Not.Large.=='>90'] <- 90.1

eGFR = eGFR %>% dplyr::select(ID,date,eGFR_val)

eGFR <- eGFR[complete.cases(eGFR),]

eGFR2 <- data.frame(ID=character(),
                  eGFR_val=character())

commonIDs <- intersect(total$ID,eGFR$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = eGFR[eGFR$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = eGFR[eGFR$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$eGFR_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest <= 90),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first <= 90),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average <= 90),"Abnormal","Normal")
    }
    # Add this 
    eGFR2 <- eGFR2 %>% add_row(ID=id,eGFR_val=value)
  }
}

eGFR <- eGFR2
rm(eGFR2)

```

#### FER - Ferritin

```{r}
FER <- read.csv(file("FER.csv"))
FER$Date.Booked.In = as.Date(FER$Date.Booked.In, format="%d/%m/%Y")
FER = FER %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
FER = FER %>%
  rename(
    FER_val = Numeric.Result
  )

FER = FER %>% dplyr::select(ID,date,FER_val)

FER <- FER[complete.cases(FER),]

FER2 <- data.frame(ID=character(),
                  FER_val=character())

commonIDs <- intersect(total$ID,FER$ID)

for (id in unique(commonIDs)){
  # Get all dates for this ID and variable
  idDates = FER[FER$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id][1]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = FER[FER$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$FER_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    age = total$Age[total$ID==id]
    gender = total$Gender[total$ID==id]

    if (gender =="M"){
      # If male
      value = if_else((lowest < 33 | highest > 490),"Abnormal","Normal")
    } else {
      # If female and < 45
      if(age <45){
        value = if_else((lowest < 15 | highest > 445),"Abnormal","Normal")
      } else {
        # If female and > 45
        value = if_else((lowest < 30 | highest > 470),"Abnormal","Normal")
      }
    }
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    age = total$Age[total$ID==id]
    gender = total$Gender[total$ID==id]

    if (gender =="M"){
      # If male
      value = if_else((first < 33 | first > 490),"Abnormal","Normal")
    } else {
      # If female and < 45
      if(age <45){
        value = if_else((first < 15 | first > 445),"Abnormal","Normal")
      } else {
        # If female and > 45
        value = if_else((first < 30 | first > 470),"Abnormal","Normal")
      }
    }
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      age = total$Age[total$ID==id]
    gender = total$Gender[total$ID==id]

    if (gender =="M"){
      # If male
      value = if_else((average < 33 | average > 490),"Abnormal","Normal")
    } else {
      # If female and < 45
      if(age <45){
        value = if_else((average < 15 | average > 445),"Abnormal","Normal")
      } else {
        # If female and > 45
        value = if_else((average < 30 | average > 470),"Abnormal","Normal")
      }
    }
    }
    # Add this 
    FER2 <- FER2 %>% add_row(ID=id,FER_val=value)
  }
}

FER <- FER2
rm(FER2)

```

#### Fib - Fibrinogen

```{r}
fib <- read.csv(file("fib.csv"))
fib$Date.Booked.In = as.Date(fib$Date.Booked.In, format="%d/%m/%Y")
fib = fib %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
fib = fib %>%
  rename(
    fib_val = Numeric.Result
  )

fib$fib_val[fib$Result..Not.Large.=='>6.0'] <- 6.1


fib = fib %>% dplyr::select(ID,date,fib_val)

fib <- fib[complete.cases(fib),]

fib2 <- data.frame(ID=character(),
                  fib_val=character())

commonIDs <- intersect(total$ID,fib$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = fib[fib$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = fib[fib$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$fib_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 1.8 | highest > 4),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 1.8 | first > 4),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 1.8 | average > 4),"Abnormal","Normal")
    }
    # Add this 
    fib2 <- fib2 %>% add_row(ID=id,fib_val=value)
  }
}

fib <- fib2
rm(fib2)

```

#### Glucose

```{r}
Glucose <- read.csv(file("Glucose.csv"))
Glucose$Date.Booked.In = as.Date(Glucose$Date.Booked.In, format="%d/%m/%Y")
Glucose = Glucose %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
Glucose = Glucose %>%
  rename(
    Glucose_val = Numeric.Result
  )

Glucose = Glucose %>% dplyr::select(ID,date,Glucose_val)

Glucose <- Glucose[complete.cases(Glucose),]

Glucose2 <- data.frame(ID=character(),
                  Glucose_val=character())

commonIDs <- intersect(total$ID,Glucose$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = Glucose[Glucose$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = Glucose[Glucose$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$Glucose_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 3 | highest > 7.8),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 3 | first > 7.8),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 3 | average > 7.8),"Abnormal","Normal")
    }
    # Add this 
    Glucose2 <- Glucose2 %>% add_row(ID=id,Glucose_val=value)
  }
}

Glucose <- Glucose2
rm(Glucose2)

```

#### HB - Hemoglobin

```{r}
HB <- read.csv(file("HB.csv"))
HB$Date.Booked.In = as.Date(HB$Date.Booked.In, format="%d/%m/%Y")
HB = HB %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
HB = HB %>%
  rename(
    HB_val = Numeric.Result
  )

HB = HB %>% dplyr::select(ID,date,HB_val)

HB <- HB[complete.cases(HB),]

HB2 <- data.frame(ID=character(),
                  HB_val=character())

commonIDs <- intersect(total$ID,HB$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = HB[HB$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = HB[HB$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$HB_val
  
  gender = total$Gender[total$ID==id]

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    if(gender == "M"){
      # If male
      value = if_else((lowest < 130 | highest > 170),"Abnormal","Normal")
    } else{
      # If female
      value = if_else((lowest < 120 | highest > 150),"Abnormal","Normal")
    }
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
     if(gender == "M"){
      # If male
      value = if_else((first < 130 | first > 170),"Abnormal","Normal")
    } else{
      # If female
      value = if_else((first < 120 | first > 150),"Abnormal","Normal")
    }
    }
    if (readingwanted == 2) {
      average = mean(all_values)
       if(gender == "M"){
      # If male
      value = if_else((average < 130 | average > 170),"Abnormal","Normal")
    } else{
      # If female
      value = if_else((average < 120 | average > 150),"Abnormal","Normal")
    }
    }
    # Add this 
    HB2 <- HB2 %>% add_row(ID=id,HB_val=value)
  }
}

HB <- HB2
rm(HB2)



```

#### HBA1c - glycated haemoglobin

```{r}
HBA1c <- read.csv(file("HBA1c.csv"))
HBA1c$Date.Booked.In = as.Date(HBA1c$Date.Booked.In, format="%d/%m/%Y")
HBA1c = HBA1c %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
HBA1c = HBA1c %>%
  rename(
    HBA1c_val = Numeric.Result
  )

HBA1c = HBA1c %>% dplyr::select(ID,date,HBA1c_val)

HBA1c <- HBA1c[complete.cases(HBA1c),]

HBA1c2 <- data.frame(ID=character(),
                  HBA1c_val=character())

commonIDs <- intersect(total$ID,HBA1c$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = HBA1c[HBA1c$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = HBA1c[HBA1c$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$HBA1c_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((highest >= 48),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first >= 48),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average >= 48),"Abnormal","Normal")
    }
    # Add this 
    HBA1c2 <- HBA1c2 %>% add_row(ID=id,HBA1c_val=value)
  }
}

HBA1c <- HBA1c2
rm(HBA1c2)
```

#### LDH - Lactate dehydrogenase

```{r}
LDH <- read.csv(file("LDH.csv"))
LDH$Date.Booked.In = as.Date(LDH$Date.Booked.In, format="%d/%m/%Y")
LDH = LDH %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
LDH = LDH %>%
  rename(
    LDH_val = Numeric.Result
  )

LDH = LDH %>% dplyr::select(ID,date,LDH_val)

LDH <- LDH[complete.cases(LDH),]

LDH2 <- data.frame(ID=character(),
                  LDH_val=character())

commonIDs <- intersect(total$ID,LDH$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = LDH[LDH$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = LDH[LDH$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$LDH_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 240 | highest > 480),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 240 | first > 480),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 240 | average > 480),"Abnormal","Normal")
    }
    # Add this 
    LDH2 <- LDH2 %>% add_row(ID=id,LDH_val=value)
  }
}

LDH <- LDH2
rm(LDH2)

```

#### PCT - Procalcitonin 

```{r}
PCT <- read.csv(file("PCT.csv"))
PCT$Date.Booked.In = as.Date(PCT$Date.Booked.In, format="%d/%m/%Y")
PCT = PCT %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
PCT = PCT %>%
  rename(
    PCT_val = Numeric.Result
  )

PCT = PCT %>% dplyr::select(ID,date,PCT_val)

PCT <- PCT[complete.cases(PCT),]

PCT2 <- data.frame(ID=character(),
                  PCT_val=character())

commonIDs <- intersect(total$ID,PCT$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = PCT[PCT$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = PCT[PCT$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$PCT_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((highest >= 0.05),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first >= 0.05),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average >= 0.05),"Abnormal","Normal")
    }
    # Add this 
    PCT2 <- PCT2 %>% add_row(ID=id,PCT_val=value)
  }
}

PCT <- PCT2
rm(PCT2)

```

#### PLT - Platelet Count

```{r}
PLT <- read.csv(file("PLT.csv"))
PLT$Date.Booked.In = as.Date(PLT$Date.Booked.In, format="%d/%m/%Y")
PLT = PLT %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
PLT = PLT %>%
  rename(
    PLT_val = Numeric.Result
  )

PLT = PLT %>% dplyr::select(ID,date,PLT_val)

PLT <- PLT[complete.cases(PLT),]

PLT2 <- data.frame(ID=character(),
                  PLT_val=character())

commonIDs <- intersect(total$ID,PLT$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = PLT[PLT$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = PLT[PLT$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$PLT_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 150 | highest > 450),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 150 | first > 450),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 150 | average > 450),"Abnormal","Normal")
    }
    # Add this 
    PLT2 <- PLT2 %>% add_row(ID=id,PLT_val=value)
  }
}

PLT <- PLT2
rm(PLT2)

```

#### Trig - Triglycerides

```{r}
trig <- read.csv(file("trig.csv"))
trig$Date.Booked.In = as.Date(trig$Date.Booked.In, format="%d/%m/%Y")
trig = trig %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
trig = trig %>%
  rename(
    trig_val = Numeric.Result
  )

trig = trig %>% dplyr::select(ID,date,trig_val)

trig <- trig[complete.cases(trig),]

trig2 <- data.frame(ID=character(),
                  trig_val=character())

commonIDs <- intersect(total$ID,trig$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = trig[trig$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = trig[trig$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$trig_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 0.5 | highest > 1.7),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 0.5 | first > 1.7),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 0.5 | average > 1.7),"Abnormal","Normal")
    }
    # Add this 
    trig2 <- trig2 %>% add_row(ID=id,trig_val=value)
  }
}

trig <- trig2
rm(trig2)

```

#### Trop - Troponin

```{r}
trop <- read.csv(file("trop.csv"))
trop$Date.Booked.In = as.Date(trop$Date.Booked.In, format="%d/%m/%Y")
trop = trop %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
trop = trop %>%
  rename(
    trop_val = Numeric.Result
  )

trop = trop %>% dplyr::select(ID,date,trop_val)

trop <- trop[complete.cases(trop),]

trop2 <- data.frame(ID=character(),
                  trop_val=character())

commonIDs <- intersect(total$ID,trop$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = trop[trop$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = trop[trop$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$trop_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((highest >= 14),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
     value = if_else((first >= 14),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
       value = if_else((average >= 14),"Abnormal","Normal")
    }
    # Add this 
    trop2 <- trop2 %>% add_row(ID=id,trop_val=value)
  }
}

trop <- trop2
rm(trop2)

```



#### FBC - Full Blood Count
Made up of:
* Lymphocytes
* Neutrophils
* White Cell Count

```{r}
FBC <- read.csv(file("FBC.csv"))
FBC$Date.Booked.In = as.Date(FBC$Date.Booked.In, format="%d/%m/%Y")
FBC = FBC %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
```

Split off Lymphocytes:

```{r}
FBCLymph = FBC %>% dplyr::select(ID,date,Result.Lymphocytes)
FBCLymph = FBCLymph %>% 
  rename(
    Lymphocytes = Result.Lymphocytes,
  )

FBCLymph = FBCLymph %>% dplyr::select(ID,date,Lymphocytes)

FBCLymph <- FBCLymph[complete.cases(FBCLymph),]

FBCLymph2 <- data.frame(ID=character(),
                  Lymphocytes=character())

commonIDs <- intersect(total$ID,FBCLymph$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = FBCLymph[FBCLymph$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = FBCLymph[FBCLymph$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$Lymphocytes

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 1.5 | highest > 4.5),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 1.5 | first > 4.5),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 1.5 | average > 4.5),"Abnormal","Normal")
    }
    # Add this 
    FBCLymph2 <- FBCLymph2 %>% add_row(ID=id,Lymphocytes=value)
  }
}

FBCLymph <- FBCLymph2
rm(FBCLymph2)

```

Split off Neutrophils:

```{r}
FBCNeutr = FBC %>% dplyr::select(ID,date,Result.Neutrophils)
FBCNeutr = FBCNeutr %>% 
  rename(
    Neutrophils = Result.Neutrophils,
  )

FBCNeutr = FBCNeutr %>% dplyr::select(ID,date,Neutrophils)

FBCNeutr <- FBCNeutr[complete.cases(FBCNeutr),]

FBCNeutr2 <- data.frame(ID=character(),
                  Neutrophils=character())

commonIDs <- intersect(total$ID,FBCNeutr$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = FBCNeutr[FBCNeutr$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = FBCNeutr[FBCNeutr$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$Neutrophils

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 2 | highest > 7.5),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 2 | first > 7.5),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 2 | average > 7.5),"Abnormal","Normal")
    }
    # Add this 
    FBCNeutr2 <- FBCNeutr2 %>% add_row(ID=id,Neutrophils=value)
  }
}

FBCNeutr <- FBCNeutr2
rm(FBCNeutr2)
```

Split off White Cell Count:

```{r}
FBCWCC = FBC %>% dplyr::select(ID,date,Result.WCC)
FBCWCC = FBCWCC %>% 
  rename(
    WCC = Result.WCC,
  )

FBCWCC = FBCWCC %>% dplyr::select(ID,date,WCC)

FBCWCC <- FBCWCC[complete.cases(FBCWCC),]

FBCWCC2 <- data.frame(ID=character(),
                  WCC=character())

commonIDs <- intersect(total$ID,FBCWCC$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = FBCWCC[FBCWCC$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = FBCWCC[FBCWCC$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$WCC

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 4 | highest > 11),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 4 | first > 11),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 4 | average > 11),"Abnormal","Normal")
    }
    # Add this 
    FBCWCC2 <- FBCWCC2 %>% add_row(ID=id,WCC=value)
  }
}

FBCWCC <- FBCWCC2
rm(FBCWCC2)

```

Split off Neutrophil to Lymphocyte Ratio

```{r}
FBCNLR = FBC %>% dplyr::select(ID,date,NLR)
FBCNLR = FBCNLR %>% 
  rename(
    NLR_val = NLR,
  )

FBCNLR = FBCNLR %>% dplyr::select(ID,date,NLR_val)

FBCNLR <- FBCNLR[complete.cases(FBCNLR),]

FBCNLR2 <- data.frame(ID=character(),
                  NLR_val=character())

commonIDs <- intersect(total$ID,FBCNLR$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = FBCNLR[FBCNLR$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = FBCNLR[FBCNLR$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$NLR_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 0.78 | highest > 3.53),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 0.78 | first> 3.53),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 0.78 | average > 3.53),"Abnormal","Normal")
    }
    # Add this 
    FBCNLR2 <- FBCNLR2 %>% add_row(ID=id,NLR_val=value)
  }
}

FBCNLR <- FBCNLR2
rm(FBCNLR2)
```

#### CovidCT - Cycle Threshold (CT) value of PCR for COVID

```{r}
CovidCT <- read.csv(file("CovidCT.csv"))
CovidCT['Measure']='CovidCT'
CovidCT$Specimen.Date = as.Date(CovidCT$Specimen.Date, format="%d/%m/%Y")
CovidCT = CovidCT %>% 
  rename(
    date = Specimen.Date,
     ID = uob_ID,
  )
```

#### Clot
Made up of:
* APTT - Activated Partial Thromboplastin Time
* PT - Prothrombin Time

```{r}
Clot <- read.csv(file("Clot.csv"))
Clot$Date.Booked.In = as.Date(Clot$Date.Booked.In, format="%d/%m/%Y")
Clot = Clot %>% 
  rename(
    date = Date.Booked.In,
     ID = uob_ID,
  )
```

Split off APTT:

```{r}
ClotAPTT = Clot %>% dplyr::select(ID,date,APTT)
ClotAPTT = ClotAPTT %>% 
  rename(
    APTT_val = APTT,
  )

ClotAPTT = ClotAPTT %>% dplyr::select(ID,date,APTT_val)

ClotAPTT <- ClotAPTT[complete.cases(ClotAPTT),]

ClotAPTT2 <- data.frame(ID=character(),
                  APTT_val=character())

commonIDs <- intersect(total$ID,ClotAPTT$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = ClotAPTT[ClotAPTT$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = ClotAPTT[ClotAPTT$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$APTT_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((highest >= 33),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first >= 33),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average >= 33),"Abnormal","Normal")
    }
    # Add this 
    ClotAPTT2 <- ClotAPTT2 %>% add_row(ID=id,APTT_val=value)
  }
}

ClotAPTT <- ClotAPTT2
rm(ClotAPTT2)
```

Split off PT:

```{r}
ClotPT = Clot %>% dplyr::select(ID,date,PT)
ClotPT = ClotPT %>% 
  rename(
    PT_val = PT,
  )
ClotPT = ClotPT %>% dplyr::select(ID,date,PT_val)

ClotPT <- ClotPT[complete.cases(ClotPT),]

ClotPT2 <- data.frame(ID=character(),
                  PT_val=character())

commonIDs <- intersect(total$ID,ClotPT$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = ClotPT[ClotPT$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = ClotPT[ClotPT$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$PT_val
  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((highest >= 13),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first >= 13),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average >= 13),"Abnormal","Normal")
    }
    # Add this 
    ClotPT2 <- ClotPT2 %>% add_row(ID=id,PT_val=value)
  }
}

ClotPT <- ClotPT2
rm(ClotPT2)
```

#### Antigen 

```{r}
Antigen <- read.csv(file("Antigen.csv"))
Antigen = Antigen %>% 
  rename(
    date = Date.of.Specimen,
     ID = uob_ID,
  )
```



#### poctLAC - Point of Care Testing - Lactate

```{r}
poctLAC <- read.csv(file("poctLAC.csv"))
#Format date
poctLAC$Date.of.Specimen = as.Date(poctLAC$Date.of.Specimen, format="%d/%m/%Y")
poctLAC = poctLAC %>% 
  rename(
    date = Date.of.Specimen,
     ID = uob_ID,
  )
poctLAC = poctLAC %>% 
  rename(
    time = Time.of.Specimen,
  )
poctLAC = poctLAC %>%
  rename(
    poctLAC_val = Numeric.Result
  )
#Combine date and time
poctLAC$dateTime = as.POSIXct(paste(poctLAC$date, poctLAC$time), format="%Y-%m-%d %H:%M:%S")
# dplyr::select relevant variables
poctLAC$date = as.Date(poctLAC$date, format="%d/%m/%Y")
poctLAC = poctLAC %>% dplyr::select(ID,date,poctLAC_val)

poctLAC <- poctLAC[complete.cases(poctLAC),]

poctLAC2 <- data.frame(ID=character(),
                  poctLAC_val=character())

commonIDs <- intersect(total$ID,poctLAC$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = poctLAC[poctLAC$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = poctLAC[poctLAC$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$poctLAC_val

  # If all_values contains any values, then proceed
    if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 0.5 | highest > 2.2),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 0.5 | first > 2.2),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 0.5 | average > 2.2),"Abnormal","Normal")
    }
    # Add this 
    poctLAC2 <- poctLAC2 %>% add_row(ID=id,poctLAC_val=value)
  }
}

poctLAC <- poctLAC2
rm(poctLAC2)


```

#### poctO2 - Point of Care Testing - O2 and CO2
Made up of:
* O2
* CO2

```{r}
poctO2 <- read.csv(file("poctO2.csv"))
```

O2:

```{r}
O2 <- poctO2 %>%
  filter(Test.Desc == "Arterial pO2")
O2$Date.of.Specimen = as.Date(O2$Date.of.Specimen, format="%d/%m/%Y")
O2 = O2 %>% 
  rename(
    date = Date.of.Specimen,
     ID = uob_ID,
  )
O2 = O2 %>% 
  rename(
    time = Time.of.Specimen,
  )
O2 = O2 %>% 
  rename(
    O2_val = Numeric.Result,
  )
#Combine date and time
O2$dateTime = as.POSIXct(paste(O2$date, O2$time), format="%Y-%m-%d %H:%M:%S")
O2 = O2 %>% dplyr::select(ID,date,O2_val)

O2 <- O2[complete.cases(O2),]

O22 <- data.frame(ID=character(),
                  O2_val=character())

commonIDs <- intersect(total$ID,O2$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = O2[O2$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = O2[O2$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$O2_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 11 | highest > 14.4),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 11 | first > 14.4),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 11 | average > 14.4),"Abnormal","Normal")
    }
    # Add this 
    O22 <- O22 %>% add_row(ID=id,O2_val=value)
  }
}

O2 <- O22
rm(O22)
```

CO2:

```{r}
CO2 <- poctO2 %>%
  filter(Test.Desc == "Arterial pCO2")
#Format date
CO2$Date.of.Specimen = as.Date(CO2$Date.of.Specimen, format="%d/%m/%Y")
CO2 = CO2 %>% 
  rename(
    date = Date.of.Specimen,
     ID = uob_ID,
  )
CO2 = CO2 %>% 
  rename(
    time = Time.of.Specimen,
  )
CO2 = CO2 %>% 
  rename(
    CO2_val = Numeric.Result,
  )
#Combine date and time
CO2$dateTime = as.POSIXct(paste(CO2$date, CO2$time), format="%Y-%m-%d %H:%M:%S")
CO2 = CO2 %>% dplyr::select(ID,date,CO2_val)

CO2 <- CO2[complete.cases(CO2),]

CO22 <- data.frame(ID=character(),
                  CO2_val=character())

commonIDs <- intersect(total$ID,CO2$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = CO2[CO2$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = CO2[CO2$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$CO2_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 4.6 | highest > 6.4),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 4.6 | first > 6.4),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 4.6 | average > 6.4),"Abnormal","Normal")
    }
    # Add this 
    CO22 <- CO22 %>% add_row(ID=id,CO2_val=value)
  }
}

CO2 <- CO22
rm(CO22)
```

#### poctpH - Point of Care Testing - pH

```{r}
poctpH <- read.csv(file("poctpH.csv"))
#Format date
poctpH$Date.of.Specimen = as.Date(poctpH$Date...Time.of.Specimen, format="%d/%m/%Y")
poctpH = poctpH %>% 
  rename(
    date = Date...Time.of.Specimen,
     ID = uob_ID,
  )
poctpH = poctpH %>% 
  rename(
    time = Time.of.Specimen,
  )
poctpH = poctpH %>% 
  rename(
    poctpH_val = Numeric.Result,
  )
#Combine date and time
poctpH$dateTime = as.POSIXct(paste(poctpH$date, poctpH$time), format="%Y-%m-%d %H:%M:%S")
poctpH$date = as.Date(poctpH$date, format="%d/%m/%Y")
poctpH = poctpH %>% dplyr::select(ID,date,poctpH_val)

poctpH <- poctpH[complete.cases(poctpH),]

poctpH2 <- data.frame(ID=character(),
                  poctpH_val=character())

commonIDs <- intersect(total$ID,poctpH$ID)


for (id in (unique(commonIDs))){
  # Get all dates for this ID and variable
  idDates = poctpH[poctpH$ID==id,]$date
    # Sort the data by date
  idDates = sort(idDates, decreasing = FALSE)
  # Find covid positive test for this ID
  idPositive = total$positiveDate[total$ID==id]
  # Get all values for this ID and variable within the daterange from positive date
  all_values = poctpH[poctpH$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$poctpH_val

  # If all_values contains any values, then proceed
  if(length(!is.na(all_values))>0 & !is.na(idPositive)) {
    if (readingwanted == 0) {
    # Determine the lowest value
    lowest = suppressWarnings(min(all_values,na.rm=TRUE))
    # Determine the highest value
    highest = suppressWarnings(max(all_values,na.rm=TRUE))
    # Compare the lowest and highest values against the range, evaluate to true if
    # either are outside the range, and assign "Abnormal", else "Normal"
    value = if_else((lowest < 7.35 | highest > 7.45),"Abnormal","Normal")
    }
    if (readingwanted == 1) {
    # select earliest test value in the list
    first <- all_values[1]
    # assign "Abnormal" if outside clinical range, else "Normal"
    value = if_else((first < 7.35 | first > 7.45),"Abnormal","Normal")
    }
    if (readingwanted == 2) {
      average = mean(all_values)
      value = if_else((average < 7.35 | average > 7.45),"Abnormal","Normal")
    }
    # Add this 
    poctpH2 <- poctpH2 %>% add_row(ID=id,poctpH_val=value)
  }
}

poctpH <- poctpH2
rm(poctpH2)
```



#### Vir - Virology

```{r}

Vir <- read.csv(file("Vir.csv"))
Vir['Measure']='Vir'
Vir$Sample.Date = as.Date(Vir$Sample.Date, format="%d/%m/%Y")
Vir = Vir %>% 
  rename(
     ID = uob_ID,
    date = Sample.Date,
    Adenovirus = Adenovirus..PCR.,
    Human_Metapneumovirus = Human.metapneumovirus..PCR.,
    Influenza_A = Influenza.A..PCR.,
    Influenza_B = Influenza.B..PCR.,
    Parainfluenza_Type_1 = Parainfluenza.Type.1..PCR.,
    Parainfluenza_Type_2 = Parainfluenza.Type.2..PCR.,
    Parainfluenza_Type_3 = Parainfluenza.Type.3..PCR.,
    Parainfluenza_Type_4 = Parainfluenza.Type.4..PCR.,
    Respiratory_Syncytial_Virus = Respiratory.Syncytial.Virus..PCR.,
    Rhinovirus = Rhinovirus..PCR.,
  )


Vir <- Vir %>% mutate(viral_coinfection = if_else((Adenovirus  == "POSITIVE" | Human_Metapneumovirus  == "POSITIVE" | Influenza_A  == "POSITIVE" | Influenza_B  == "POSITIVE" | Parainfluenza_Type_1  == "POSITIVE" | Parainfluenza_Type_2  == "POSITIVE" | Parainfluenza_Type_3  == "POSITIVE" | Parainfluenza_Type_4  == "POSITIVE" | Respiratory_Syncytial_Virus  == "POSITIVE" | Rhinovirus  == "POSITIVE"),TRUE,FALSE))

Vir <- Vir %>% dplyr::select(ID,date,viral_coinfection)

Vir <- Vir[complete.cases(Vir),]

Vir2 <- data.frame(ID=character(),
                  viral_coinfection=logical())

commonIDs <- intersect(total$ID,Vir$ID)

for (id in unique(commonIDs)){
    # Return all values for the admission date for this ID
    # Find the average value for these dates
    # Store in new table for that variable where we have one value per date per
  idDates = Vir[Vir$ID==id,]$date
  idPositive = total$positiveDate[total$ID==id]
  presence = TRUE %in% (Vir[Vir$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$viral_coinfection)
  Vir2 <- Vir2 %>% add_row(ID=id,viral_coinfection=presence)

}

Vir <- Vir2
rm(Vir2)


```


#### BC

```{r}
BC <- read.csv(file("BC.csv"))
BC['Measure']='BC'
BC$Date.of.Specimen = as.Date(BC$Date.of.Specimen, format="%d/%m/%Y")
BC = BC %>% 
  rename(
    date = Date.of.Specimen,
     ID = uob_ID,
  )

BC <- BC %>% mutate(bc_coinfection = if_else((Organism.Desc != "Negative BC" & Source.Desc != "? Contaminant"),TRUE,FALSE))

BC <- BC %>% dplyr::select(ID,date,bc_coinfection)

BC <- BC[complete.cases(BC),]

BC2 <- data.frame(ID=character(),
                  bc_coinfection=logical())

commonIDs <- intersect(total$ID,Vir$ID)

for (id in unique(commonIDs)){
    # Return all values for the admission date for this ID
    # Find the average value for these dates
    # Store in new table for that variable where we have one value per date per
  idDates = BC[BC$ID==id,]$date
  idPositive = total$positiveDate[total$ID==id]
  presence = TRUE %in% (BC[BC$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$bc_coinfection)
  BC2 <- BC2 %>% add_row(ID=id,bc_coinfection=presence)

}

BC <- BC2
rm(BC2)


```

#### Resp

```{r}
Resp <- read.csv(file("Resp.csv"))
Resp['Measure']='Resp'
Resp$Date.of.Specimen = as.Date(Resp$Date.of.Specimen, format="%d/%m/%Y")
Resp = Resp %>% 
  rename(
     ID = uob_ID,
    date = Date.of.Specimen,
  )

Resp <- Resp %>% mutate(resp_coinfection = if_else((Organism.Desc != "Negative Sp"),TRUE,FALSE))

Resp <- Resp %>% dplyr::select(ID,date,resp_coinfection)

Resp <- Resp[complete.cases(Resp),]

Resp2 <- data.frame(ID=character(),
                  resp_coinfection=logical())

commonIDs <- intersect(total$ID,Vir$ID)

for (id in unique(commonIDs)){
    # Return all values for the admission date for this ID
    # Find the average value for these dates
    # Store in new table for that variable where we have one value per date per
  idDates = Resp[Resp$ID==id,]$date
  idPositive = total$positiveDate[total$ID==id]
  presence = TRUE %in% (Resp[Resp$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$resp_coinfection)
  Resp2 <- Resp2 %>% add_row(ID=id,resp_coinfection=presence)

}

Resp <- Resp2
rm(Resp2)
```

#### Urine

```{r}
Urine <- read.csv(file("Urine.csv"))
Urine['Measure']='Urine'
Urine$Date.of.Specimen = as.Date(Urine$Date.of.Specimen, format="%d/%m/%Y")
Urine = Urine %>% 
  rename(
     ID = uob_ID,
    date = Date.of.Specimen,
  )

Urine <- Urine %>% mutate(urine_coinfection = if_else((Organism.Desc != "Negative MSU"),TRUE,FALSE))

Urine <- Urine %>% dplyr::select(ID,date,urine_coinfection)

Urine <- Urine[complete.cases(Urine),]

Urine2 <- data.frame(ID=character(),
                  urine_coinfection=logical())

commonIDs <- intersect(total$ID,Vir$ID)

for (id in unique(commonIDs)){
    # Return all values for the admission date for this ID
    # Find the average value for these dates
    # Store in new table for that variable where we have one value per date per
  idDates = Urine[Urine$ID==id,]$date
  idPositive = total$positiveDate[total$ID==id]
  presence = TRUE %in% (Urine[Urine$ID==id,][(idDates >= idPositive & idDates < (idPositive + dateRange)),]$urine_coinfection)
  Urine2 <- Urine2 %>% add_row(ID=id,urine_coinfection=presence)

}

Urine <- Urine2
rm(Urine2)

```



# Merge values with total table by admission date

```{r}
variables = list(BE,BNP,CRP,DDM,eGFR,FER,fib,Glucose,HB,HBA1c,LDH,PCT,PLT,trig,trop,FBCLymph,FBCNeutr,FBCWCC,FBCNLR,ClotAPTT,ClotPT,poctLAC,O2,CO2,poctpH,Vir,BC,Resp,Urine)

for (variable in variables){
  total <- merge(total,variable, all.x=TRUE)
}

```

#### Add any co-infection column 
```{r}
total <- total %>% mutate(coinfection = if_else((viral_coinfection == TRUE | resp_coinfection == TRUE | bc_coinfection == TRUE | urine_coinfection == TRUE),TRUE,FALSE,FALSE))
totalBinary <- total
```

#### Comorbidities
```{r}
AvonCap <- read.csv(file("AvonCap.csv"))
AvonCap = AvonCap %>% rename(ID = uob_ID)
AvonCap <- AvonCap[!duplicated(AvonCap$ID),]
AvonCap <- subset(AvonCap, select = -c(Repeat.Instrument,Repeat.Instance,
                                       COVID.19.diagnosis))
AvonCap = AvonCap %>%
    rename(
        Community.Pneumonia.Radio = Final.Standard.of.Care.LRTD.related.diagnosis..choice.CAP...radiologically.confirmed.,
        Community.Pneumonia.Clin = Final.Standard.of.Care.LRTD.related.diagnosis..choice.CAP...clinically.confirmed..but.not.on.radiology..,
        Community.Acquired.Pneumonia.No = Final.Standard.of.Care.LRTD.related.diagnosis..choice.CAP...no.radiology.performed.,
        Acute_bronchitis = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Acute.bronchitis.,
        Exacerbation_of_COPD = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Exacerbation.of.COPD.,
        Empyema_lung_abscess = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Empyema.lung.abscess.,
        LRTI_not_further_specified = Final.Standard.of.Care.LRTD.related.diagnosis..choice.LRTI...not.further.specified.,
        Congestive_heart_failure = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Congestive.heart.failure.,
        Non_infectious_process = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Non.infectious.process.,
        Non_LRTD_infection_related_diagnosis = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Non.LRTD.infection.related.diagnosis.,
        Oth.LRTI.Specified =
        Final.Standard.of.Care.LRTD.related.diagnosis..choice.Other.LRTI.specified.,
        NYHA_Heart_failure = NYHA...Heart.Failure..nbsp.,
        CRB65_Score = CRB65.Score,
        NEWS2_Score = NEWS.2.Score,
        Respiratory_Disease_None = Respiratory.Disease..choice.None.,
        COPD = Respiratory.Disease..choice.COPD..Chronic.Obstructive.Pulmonary.Disease.Emphysema..,
        Asthma = Respiratory.Disease..choice.Asthma.,
        Bronchiectasis = Respiratory.Disease..choice.Bronchiectasis.,
        Pulmonary_Fibrosis_Interstitial_Lung_Disease = Respiratory.Disease..choice.Pulmonary.Fibrosis.Interstitial.Lung.Disease.,
        Respiratory_Disease_other = Respiratory.Disease..choice.Other.,
        Chronic_heart_disease_none = Chronic.Heart.Disease..choice.None.,
        Hypertension = Chronic.Heart.Disease..choice.Hypertension.,
        Atrial_Fibrillation = Chronic.Heart.Disease..choice.Atrial.Fibrillation.,
        Ischaemic_heart_disease = Chronic.Heart.Disease..choice.Ischaemic.heart.disease.,
        Heart_failure = Chronic.Heart.Disease..choice.Heart.failure.CCF.,
        Chronic_heart_disease_other = Chronic.Heart.Disease..choice.Other.,
        Chronic_Kidney_Disease = Chronic.Kidney.Disease..CKD..Mod.Severe..eGFR..30..Cr.265.umol.L..dialysis..transplantation..uremic.syndrome,
        Liver_disease = Liver.Disease.Mild...nbsp.cirrhosis.without.portal.HTN..chronic.hepatitis..Mod.Severe...nbsp.cirrhosis.with.portal.HTN.....variceal.bleeding,
        Diabetes = Diabetes,
        Cognitive_Impairment_Dementia_none = Cognitive.Impairment.Dementia..choice.None.,
        Dementia = Cognitive.Impairment.Dementia..choice.Dementia.,
        Cognitive_impairment = Cognitive.Impairment.Dementia..choice.Cognitive.Impairment.,
        CVA_Stroke = Cognitive.Impairment.Dementia..choice.CVA..stroke..,
        TIA_mini_stroke = Cognitive.Impairment.Dementia..choice.TIA..mini.stroke..,
        Hemiplegiahemiplegia_or_paraplegia = Hemiplegiahemiplegia.or.paraplegia,
        Peripheral_vascular_disease = Peripheral.Vascular.Disease.Intermittent.claudication..periph..arterial.bypass.for.insufficiency..gangrene..acute.arterial.insufficiency..untreated.aneurysm....6cm..nbsp.,
        Immunosuppressive_medication = Immunosuppressive.Medication.includes.oral.steroids..biologics..chemotherapy.,
        Immunodeficiency = Immunodeficiency.eg.SCID..hypogammaglobulinaemia..splenectomy.,
        Connective_tissue_disease = Connective.Tissue.Disease..SLE..polymyositis..mixed.nbsp.Connective.Tissue.Disease..polymyalgia.rheumatica..moderate.to.severe.Rheumatoid.Arthritis.,
        HIV_negative_or_not_tested = HIV.status..choice.Negative..no.HIV...or.not.tested.,
        HIV_positive = HIV.status..choice.HIV.,
        AIDS = HIV.status..choice.AIDS.,
        Solid_organ_cancer_malignancy = Solid.Organ.Cancer.Malignancy.Initially.treated.in.the.last.5.years.exclude.non.melanomatous.skin.cancers.and.in.situ.cervical.carcinoma,
        Haematological_malignancy_leukaemia_none = Haematological.Malignancy.Leukaemia...nbsp.CML..CLL..AML..ALL..Polycythaemia.Vera.Lymphoma...nbsp.NHL..Hodgkin.s..Waldenstr.m..multiple.myeloma...choice.None.,
        Leukaemia = Haematological.Malignancy.Leukaemia...nbsp.CML..CLL..AML..ALL..Polycythaemia.Vera.Lymphoma...nbsp.NHL..Hodgkin.s..Waldenstr.m..multiple.myeloma...choice.Leukaemia.,
        Lymphoma = Haematological.Malignancy.Leukaemia...nbsp.CML..CLL..AML..ALL..Polycythaemia.Vera.Lymphoma...nbsp.NHL..Hodgkin.s..Waldenstr.m..multiple.myeloma...choice.Lymphoma.,
        Organ_transplantation = Organ.Transplantation,
        Pregnancy_post_partum = Pregnancy.Post.partum,
        Gastric_Duodenal_Ulcer_disease = Gastric.Duodenal.Ulcer.Disease.Patients.who.have.required.treatment.for.PUD.nbsp.,
        Rockwood_frailty_score = Rockwood.Frailty.Score,
        Radiology_result = Radiology.Result
    )
AvonCap <- subset(AvonCap, select = c(ID,PSI,
                                      NYHA_Heart_failure,CRB65_Score,
                                      NEWS2_Score,COPD,Asthma,Bronchiectasis,
                                      Respiratory_Disease_other, Hypertension,
                                      Chronic_Kidney_Disease,Liver_disease,
                                      Diabetes,CVA_Stroke,TIA_mini_stroke,
                                      Immunodeficiency, HIV_positive))
totalBinary <- merge(total,AvonCap,by=c("ID"),all.x=TRUE)

```

# Check values against ranges and create normal/abnormal binary column
This is done here because many values depend on age and gender, so more convenient. 

* BE (higher or lower) -  ambiguous
* BNP (higher) -  clear
* APTT (higher) -  clear
* PT (higher) -  clear
* CO2 (lower or higher) -  ambiguous
* O2 (lower or higher) -  ambiguous
* CRP (higher) -  clear
* DDM (higher) -  clear
* eGFR (lower) 0  clear
* Lymphocytes (lower or higher) -  ambiguous
* Neutrophils (lower or higher) -  ambiguous 
* NLR (lower or higher) -  ambiguous
* WCC (lower or higher) -  ambiguous
* FER (lower or higher) -  ambiguous
* fib (lower or higher) -  ambiguous
* Glucose (lower or higher) -  ambiguous
* HB (lower or higher) -  ambiguous
* HBA1c (higher) -  clear
* LDH (lower or higher) -  ambiguous
* PCT (higher) -  clear
* PLT (lower or higher) -  ambiguous
* Lactate (higher) -  clear
* pH (lower or higher) -  ambiguous
* trig (lower or higher) -  ambiguous
* trop (higher) -  clear



# Missingness

```{r}
drop <- c("ID","admissionDate","dischargeDate","Gender","Age","died","went_to_icu","severeOutcome")
missingData = total[,!(names(total) %in% drop)]
missingData %>% ff_glimpse()
missingData %>% missing_plot()
```


# Replace NAs for columns with "Test not taken"
```{r}
#replaceNAs_totalBinary <- totalBinary %>% dplyr::select(-ID,-admissionDate,-dischargeDate,-ITU_End,-ITU_Start,-deathDate,-Gender,-Age,-died,-went_to_icu,-severeOutcome,-positiveDate,-coinfection) %>% replace_na("Test not taken")

totalBinary[c("BE_val","BNP_val","CRP_val","DDM_val","eGFR_val","FER_val","fib_val","Glucose_val","HB_val","HBA1c_val","LDH_val","PCT_val","PLT_val","trig_val","trop_val","Lymphocytes","Neutrophils","WCC","NLR_val","APTT_val","PT_val","poctLAC_val","O2_val","CO2_val","poctpH_val","viral_coinfection","bc_coinfection","resp_coinfection","urine_coinfection")][is.na(totalBinary[c("BE_val","BNP_val","CRP_val","DDM_val","eGFR_val","FER_val","fib_val","Glucose_val","HB_val","HBA1c_val","LDH_val","PCT_val","PLT_val","trig_val","trop_val","Lymphocytes","Neutrophils","WCC","NLR_val","APTT_val","PT_val","poctLAC_val","O2_val","CO2_val","poctpH_val","viral_coinfection","bc_coinfection","resp_coinfection","urine_coinfection")])] <- "Test not taken"
```

COVID on admission
```{r}
totalBinary$OnAdmission <- with(totalBinary, ifelse(positiveDate-admissionDate >=8,
                                                    FALSE,TRUE))
```


```{r}
if (dateRange==1) {
    if (readingwanted==0) {
write.csv(x=totalBinary, file="totalBinary1worst.csv")
  }
    if (readingwanted==1) {
write.csv(x=totalBinary, file="totalBinary1first.csv")
  }
    if (readingwanted==2) {
write.csv(x=totalBinary, file="totalBinary1mean.csv")
  }
}
if (dateRange==3) {
 if (readingwanted==0) {
write.csv(x=totalBinary, file="totalBinary3worst.csv")
  }
    if (readingwanted==1) {
write.csv(x=totalBinary, file="totalBinary3first.csv")
  }
    if (readingwanted==2) {
write.csv(x=totalBinary, file="totalBinary3mean.csv")
  }
}
if (dateRange==5) {
 if (readingwanted==0) {
write.csv(x=totalBinary, file="totalBinary5worst.csv")
  }
    if (readingwanted==1) {
write.csv(x=totalBinary, file="totalBinary5first.csv")
  }
    if (readingwanted==2) {
write.csv(x=totalBinary, file="totalBinary5mean.csv")
  }
}
```

