---
title: "R Notebook"
output: html_notebook
---
# LABMARCS Visualisation
## Libraries

```{r}
library(ggplot2)
library(hrbrthemes)
library(tidyverse)
library(plotly)
library(BBmisc)
library(scales)
library(dplyr)
library(naniar)
library(gridExtra)
library(knitr)
library(moments)
library(formattable)
library(IRdisplay)
library(repr)
library(data.table)
library(DescTools)
```

## Load in data files
### Outcome data
#### NBT Outcomes

```{r}
NBT_outcomes <- read.csv(file("NBT_outcomes.csv"))
NBT_outcomes = NBT_outcomes %>% 
  rename(
    admissionDate = admission_date,
  )
NBT_outcomes$admissionDate = as.Date(NBT_outcomes$admissionDate, format="%d/%m/%Y")
NBT_outcomes = NBT_outcomes %>% 
  rename(
    dischargeDate = discharge_date,
  )
NBT_outcomes$dischargeDate = as.Date(NBT_outcomes$dischargeDate, format="%d/%m/%Y")
NBT_outcomes_deaths = NBT_outcomes %>%
  filter(DischargeOutcomeDesc == "Patient Died")
NBT_outcomes_deaths$deathDate = NBT_outcomes_deaths$dischargeDate
NBT_outcomes <- merge(NBT_outcomes,NBT_outcomes_deaths,all=TRUE)
NBT_outcomes$ITU_Start = as.Date(NBT_outcomes$ITU_Start, format="%d/%m/%Y")
NBT_outcomes$ITU_End = as.Date(NBT_outcomes$ITU_End, format="%d/%m/%Y")
NBT_outcomes2 = NBT_outcomes %>% select(ID,admissionDate,dischargeDate,ITU_Start,ITU_End,deathDate)
```

#### UHB Outcomes

```{r}
UHB_outcomes1 <- read.csv(file("UHB_outcomes1.csv"))
UHB_outcomes1 = UHB_outcomes1 %>% 
  rename(
    admissionDate = attend_date,
  )
UHB_outcomes1$admissionDate = as.Date(UHB_outcomes1$admissionDate, format="%d/%m/%Y")
UHB_outcomes1$dischargeDate = as.Date(UHB_outcomes1$admissionDate + as.integer(UHB_outcomes1$hospital_length_of_stay))
UHB_outcomes1 = UHB_outcomes1 %>% 
  rename(
    deathDate = fu_death_date,
  )
UHB_outcomes1$deathDate = as.Date(UHB_outcomes1$deathDate, format="%d/%m/%Y")
UHB_outcomes1$ITU_Start <- as.Date(NA)
UHB_outcomes1$ITU_End <- as.Date(NA)
UHB_outcomes12 = UHB_outcomes1 %>% select(ID,admissionDate,dischargeDate,ITU_Start,ITU_End,deathDate)

UHB_outcomes2 <- read.csv(file("UHB_outcomes2.csv"))
UHB_outcomes2 = UHB_outcomes2 %>% 
  rename(
    admissionDate = attend_dte,
  )
UHB_outcomes2$admissionDate = as.Date(UHB_outcomes2$admissionDate, format="%d/%m/%Y")
UHB_outcomes2 = UHB_outcomes2 %>% 
  rename(
    dischargeDate = outcome_dte,
  )
UHB_outcomes2$dischargeDate = as.Date(UHB_outcomes2$dischargeDate, format="%d/%m/%Y")
UHB_outcomes2_deaths = UHB_outcomes2 %>%
  filter(outcome == 3)
UHB_outcomes2_deaths$deathDate = UHB_outcomes2_deaths$dischargeDate
UHB_outcomes2 <- merge(UHB_outcomes2,UHB_outcomes2_deaths,all=TRUE)
UHB_outcomes2$ITU_Start <- as.Date(NA)
UHB_outcomes2$ITU_End <- as.Date(NA)
UHB_outcomes22 = UHB_outcomes2 %>% select(ID,admissionDate,dischargeDate,ITU_Start,ITU_End,deathDate)
```

#### Weston Outcomes

```{r}
WestonOutcomes <- read.csv(file("Weston Outcomes.csv"))
WestonOutcomes = WestonOutcomes %>% 
  rename(
    admissionDate = Admission.date,
  )
WestonOutcomes$admissionDate = as.Date(WestonOutcomes$admissionDate, format="%d/%m/%Y")
WestonOutcomes = WestonOutcomes %>% 
  rename(
    dischargeDate = Discharge.date,
  )
WestonOutcomes$dischargeDate = as.Date(WestonOutcomes$dischargeDate, format="%d/%m/%Y")
WestonOutcomes = WestonOutcomes %>% 
  rename(
    ITU_Start = ICU.Admission.Date
  )
WestonOutcomes$ITU_Start = as.Date(WestonOutcomes$ITU_Start, format="%d/%m/%Y")
WestonOutcomes = WestonOutcomes %>% 
  rename(
    ITU_End = ICU.Discharge.Date
  )
WestonOutcomes$ITU_End = as.Date(WestonOutcomes$ITU_End, format="%d/%m/%Y")
WestonOutcomes = WestonOutcomes %>% 
  rename(
    deathDate = Date.of.Death
  )
WestonOutcomes$deathDate = as.Date(WestonOutcomes$deathDate, format="%d/%m/%Y")
WestonOutcomes2 = WestonOutcomes %>% select(ID,admissionDate,dischargeDate,ITU_Start,ITU_End,deathDate)
```

### Merge Outcome data

```{r}
# Merge outcomes data
totalOutcomes <- rbind(UHB_outcomes12,UHB_outcomes22,NBT_outcomes2,WestonOutcomes2)
totalOutcomes$deathDate = as.Date(totalOutcomes$deathDate, format="%d/%m/%Y")
totalOutcomes$ITU_Start = as.Date(totalOutcomes$ITU_Start, format="%d/%m/%Y")
totalOutcomes$ITU_End = as.Date(totalOutcomes$ITU_End, format="%d/%m/%Y")
totalOutcomes$dischargeDate = as.Date(totalOutcomes$dischargeDate, format="%d/%m/%Y")
```

### Load variable data
Data is loaded in from csv, and then all dates are renamed as well as the actual values for each variable, so that they have common column names for merging data together. 
#### BE - Bicarbonate Excess

```{r}
BE <- read.csv(file("BE.csv"))
BE$Date.Booked.In = as.Date(BE$Date.Booked.In, format="%d/%m/%Y")
BE = BE %>% 
  rename(
    date = Date.Booked.In,
  )
BE = BE %>%
  rename(
    BE_val = Numeric.Result
  )
```

#### BNP - B-type natriuretic peptide

```{r}
BNP <- read.csv(file("BNP.csv"))
BNP$Date.Booked.In = as.Date(BNP$Date.Booked.In, format="%d/%m/%Y")
BNP = BNP %>% 
  rename(
    date = Date.Booked.In,
  )
BNP = BNP %>%
  rename(
    BNP_val = Numeric.Result
  )
```

#### CRP - C-Reactive Protein

```{r}
CRP <- read.csv(file("CRP.csv"))
CRP$Date.Booked.In = as.Date(CRP$Date.Booked.In, format="%d/%m/%Y")
CRP = CRP %>% 
  rename(
    date = Date.Booked.In,
  )
CRP = CRP %>%
  rename(
    CRP_val = Numeric.Result
  )
```

#### CovidCT - Cycle Threshold (CT) value of PCR for COVID

```{r}
CovidCT <- read.csv(file("CovidCT.csv"))
CovidCT['Measure']='CovidCT'
CovidCT$Specimen.Date = as.Date(CovidCT$Specimen.Date, format="%d/%m/%Y")
CovidCT = CovidCT %>% 
  rename(
    date = Specimen.Date,
  )
```

#### DDM - D-Dimer 

```{r}
DDM <- read.csv(file("DDM.csv"))
DDM$Date.Booked.In = as.Date(DDM$Date.Booked.In, format="%d/%m/%Y")
DDM = DDM %>% 
  rename(
    date = Date.Booked.In,
  )
DDM = DDM %>%
  rename(
    DDM_val = Numeric.Result
  )
```

#### eGFR - Estimated Glomerular Filtration Rate

```{r}
eGFR <- read.csv(file("eGFR.csv"))
eGFR$Date.Booked.In = as.Date(eGFR$Date.Booked.In, format="%d/%m/%Y")
eGFR = eGFR %>% 
  rename(
    date = Date.Booked.In,
  )
eGFR = eGFR %>%
  rename(
    eGFR_val = Numeric.Result
  )
```

#### FER - Ferritin

```{r}
FER <- read.csv(file("FER.csv"))
FER$Date.Booked.In = as.Date(FER$Date.Booked.In, format="%d/%m/%Y")
FER = FER %>% 
  rename(
    date = Date.Booked.In,
  )
FER = FER %>%
  rename(
    FER_val = Numeric.Result
  )
```

#### Fib - Fibrinogen

```{r}
fib <- read.csv(file("fib.csv"))
fib$Date.Booked.In = as.Date(fib$Date.Booked.In, format="%d/%m/%Y")
fib = fib %>% 
  rename(
    date = Date.Booked.In,
  )
fib = fib %>%
  rename(
    fib_val = Numeric.Result
  )
```

#### Glucose

```{r}
Glucose <- read.csv(file("Glucose.csv"))
Glucose$Date.Booked.In = as.Date(Glucose$Date.Booked.In, format="%d/%m/%Y")
Glucose = Glucose %>% 
  rename(
    date = Date.Booked.In,
  )
Glucose = Glucose %>%
  rename(
    Glucose_val = Numeric.Result
  )
```

#### HB - Hemoglobin

```{r}
HB <- read.csv(file("HB.csv"))
HB$Date.Booked.In = as.Date(HB$Date.Booked.In, format="%d/%m/%Y")
HB = HB %>% 
  rename(
    date = Date.Booked.In,
  )
HB = HB %>%
  rename(
    HB_val = Numeric.Result
  )
```

#### HBA1c - glycated haemoglobin

```{r}
HBA1c <- read.csv(file("HBA1c.csv"))
HBA1c$Date.Booked.In = as.Date(HBA1c$Date.Booked.In, format="%d/%m/%Y")
HBA1c = HBA1c %>% 
  rename(
    date = Date.Booked.In,
  )
HBA1c = HBA1c %>%
  rename(
    HBA1c_val = Numeric.Result
  )
```

#### LDH - Lactate dehydrogenase

```{r}
LDH <- read.csv(file("LDH.csv"))
LDH$Date.Booked.In = as.Date(LDH$Date.Booked.In, format="%d/%m/%Y")
LDH = LDH %>% 
  rename(
    date = Date.Booked.In,
  )
LDH = LDH %>%
  rename(
    LDH_val = Numeric.Result
  )
```

#### PCT - Procalcitonin 

```{r}
PCT <- read.csv(file("PCT.csv"))
PCT$Date.Booked.In = as.Date(PCT$Date.Booked.In, format="%d/%m/%Y")
PCT = PCT %>% 
  rename(
    date = Date.Booked.In,
  )
PCT = PCT %>%
  rename(
    PCT_val = Numeric.Result
  )
```

#### PLT - Platelet Count

```{r}
PLT <- read.csv(file("PLT.csv"))
PLT$Date.Booked.In = as.Date(PLT$Date.Booked.In, format="%d/%m/%Y")
PLT = PLT %>% 
  rename(
    date = Date.Booked.In,
  )
PLT = PLT %>%
  rename(
    PLT_val = Numeric.Result
  )
```

#### Trig - Triglycerides

```{r}
trig <- read.csv(file("trig.csv"))
trig$Date.Booked.In = as.Date(trig$Date.Booked.In, format="%d/%m/%Y")
trig = trig %>% 
  rename(
    date = Date.Booked.In,
  )
trig = trig %>%
  rename(
    trig_val = Numeric.Result
  )
```

#### Trop - Troponin

```{r}
trop <- read.csv(file("trop.csv"))
trop$Date.Booked.In = as.Date(trop$Date.Booked.In, format="%d/%m/%Y")
trop = trop %>% 
  rename(
    date = Date.Booked.In,
  )
trop = trop %>%
  rename(
    trop_val = Numeric.Result
  )
```

#### Vir - Virology

```{r}
Vir <- read.csv(file("Vir.csv"))
Vir['Measure']='Vir'
Vir$Sample.Date = as.Date(Vir$Sample.Date, format="%d/%m/%Y")
Vir = Vir %>% 
  rename(
    date = Sample.Date,
  )
Vir = Vir %>% 
  rename(
    Adenovirus = Adenovirus..PCR.,
  )
Vir = Vir %>% 
  rename(
    Human_Metapneumovirus = Human.metapneumovirus..PCR.,
  )
Vir = Vir %>% 
  rename(
    Influenza_A = Influenza.A..PCR.,
  )
Vir = Vir %>% 
  rename(
    Influenza_B = Influenza.B..PCR.,
  )
Vir = Vir %>% 
  rename(
    Parainfluenza_Type_1 = Parainfluenza.Type.1..PCR.,
  )
Vir = Vir %>% 
  rename(
    Parainfluenza_Type_2 = Parainfluenza.Type.2..PCR.,
  )
Vir = Vir %>% 
  rename(
    Parainfluenza_Type_3 = Parainfluenza.Type.3..PCR.,
  )
Vir = Vir %>% 
  rename(
    Parainfluenza_Type_4 = Parainfluenza.Type.4..PCR.,
  )
Vir = Vir %>% 
  rename(
    Respiratory_Syncytial_Virus = Respiratory.Syncytial.Virus..PCR.,
  )
Vir = Vir %>% 
  rename(
    Rhinovirus = Rhinovirus..PCR.,
  )
```

#### FBC - Full Blood Count
Made up of:
* Lymphocytes
* Neutrophils
* White Cell Count

```{r}
FBC <- read.csv(file("FBC.csv"))
FBC$Date.Booked.In = as.Date(FBC$Date.Booked.In, format="%d/%m/%Y")
FBC = FBC %>% 
  rename(
    date = Date.Booked.In,
  )
```

Split off Lymphocytes:

```{r}
FBCLymph = FBC %>% select(ID,date,Result.Lymphocytes)
FBCLymph = FBCLymph %>% 
  rename(
    Lymphocytes = Result.Lymphocytes,
  )
```

Split off Neutrophils:

```{r}
FBCNeutr = FBC %>% select(ID,date,Result.Neutrophils)
FBCNeutr = FBCNeutr %>% 
  rename(
    Neutrophils = Result.Neutrophils,
  )
```

Split off White Cell Count:

```{r}
FBCWCC = FBC %>% select(ID,date,Result.WCC)
FBCWCC = FBCWCC %>% 
  rename(
    WCC = Result.WCC,
  )
```

Split off Neutrophil to Lymphocyte Ratio

```{r}
FBCNLR = FBC %>% select(ID,date,NLR)
FBCNLR = FBCNLR %>% 
  rename(
    NLR_val = NLR,
  )
```

#### CovidCT - Cycle Threshold (CT) value of PCR for COVID

```{r}
CovidCT <- read.csv(file("CovidCT.csv"))
CovidCT['Measure']='CovidCT'
CovidCT$Specimen.Date = as.Date(CovidCT$Specimen.Date, format="%d/%m/%Y")
CovidCT = CovidCT %>% 
  rename(
    date = Specimen.Date,
  )
```

#### Clot
Made up of:
* APTT - Activated Partial Thromboplastin Time
* PT - Prothrombin Time

```{r}
Clot <- read.csv(file("Clot.csv"))
Clot$Date.Booked.In = as.Date(Clot$Date.Booked.In, format="%d/%m/%Y")
Clot = Clot %>% 
  rename(
    date = Date.Booked.In,
  )
```

Split off APTT:

```{r}
ClotAPTT = Clot %>% select(ID,date,APTT)
ClotAPTT = ClotAPTT %>% 
  rename(
    APTT_val = APTT,
  )
```

Split off PT:

```{r}
ClotPT = Clot %>% select(ID,date,PT)
ClotPT = ClotPT %>% 
  rename(
    PT_val = PT,
  )
```

#### Antigen 

```{r}
Antigen <- read.csv(file("Antigen.csv"))
Antigen = Antigen %>% 
  rename(
    date = Date.of.Specimen,
  )
```

#### BC

```{r}
BC <- read.csv(file("BC.csv"))
BC['Measure']='BC'
BC$Date.of.Specimen = as.Date(BC$Date.of.Specimen, format="%d/%m/%Y")
BC = BC %>% 
  rename(
    date = Date.of.Specimen,
  )
```

#### Resp

```{r}
Resp <- read.csv(file("Resp.csv"))
Resp['Measure']='Resp'
Resp$Date.of.Specimen = as.Date(Resp$Date.of.Specimen, format="%d/%m/%Y")
Resp = Resp %>% 
  rename(
    date = Date.of.Specimen,
  )
```

#### Urine

```{r}
Urine <- read.csv(file("Urine.csv"))
Urine['Measure']='Urine'
Urine$Date.of.Specimen = as.Date(Urine$Date.of.Specimen, format="%d/%m/%Y")
Urine = Urine %>% 
  rename(
    date = Date.of.Specimen,
  )
```

#### poctLAC - Point of Care Testing - Lactate

```{r}
poctLAC <- read.csv(file("poctLAC.csv"))
#Format date
poctLAC$Date.of.Specimen = as.Date(poctLAC$Date.of.Specimen, format="%d/%m/%Y")
poctLAC = poctLAC %>% 
  rename(
    date = Date.of.Specimen,
  )
poctLAC = poctLAC %>% 
  rename(
    time = Time.of.Specimen,
  )
poctLAC = poctLAC %>%
  rename(
    poctLAC_val = Numeric.Result
  )
#Combine date and time
poctLAC$dateTime = as.POSIXct(paste(poctLAC$date, poctLAC$time), format="%Y-%m-%d %H:%M:%S")
# Select relevant variables
```

#### poctO2 - Point of Care Testing - O2 and CO2
Made up of:
* O2
* CO2

```{r}
poctO2 <- read.csv(file("poctO2.csv"))
```

O2:

```{r}
O2 <- poctO2 %>%
  filter(Test.Desc == "Arterial pO2")
O2$Date.of.Specimen = as.Date(O2$Date.of.Specimen, format="%d/%m/%Y")
O2 = O2 %>% 
  rename(
    date = Date.of.Specimen,
  )
O2 = O2 %>% 
  rename(
    time = Time.of.Specimen,
  )
O2 = O2 %>% 
  rename(
    O2_val = Numeric.Result,
  )
#Combine date and time
O2$dateTime = as.POSIXct(paste(O2$date, O2$time), format="%Y-%m-%d %H:%M:%S")
```

CO2:

```{r}
CO2 <- poctO2 %>%
  filter(Test.Desc == "Arterial pCO2")
#Format date
CO2$Date.of.Specimen = as.Date(CO2$Date.of.Specimen, format="%d/%m/%Y")
CO2 = CO2 %>% 
  rename(
    date = Date.of.Specimen,
  )
CO2 = CO2 %>% 
  rename(
    time = Time.of.Specimen,
  )
CO2 = CO2 %>% 
  rename(
    CO2_val = Numeric.Result,
  )
#Combine date and time
CO2$dateTime = as.POSIXct(paste(CO2$date, CO2$time), format="%Y-%m-%d %H:%M:%S")
```

#### poctpH - Point of Care Testing - pH

```{r}
poctpH <- read.csv(file("poctpH.csv"))
#Format date
poctpH$Date.of.Specimen = as.Date(poctpH$Date...Time.of.Specimen, format="%d/%m/%Y")
poctpH = poctpH %>% 
  rename(
    date = Date...Time.of.Specimen,
  )
poctpH = poctpH %>% 
  rename(
    time = Time.of.Specimen,
  )
poctpH = poctpH %>% 
  rename(
    poctpH_val = Numeric.Result,
  )
#Combine date and time
poctpH$dateTime = as.POSIXct(paste(poctpH$date, poctpH$time), format="%Y-%m-%d %H:%M:%S")
```

## AvonCap
Names of all of these comorbidities are verbose and confusing, so shortened to make easier to understand. 

```{r}
AvonCap <- read.csv(file("AvonCap.csv"))
AvonCap = AvonCap %>%
    rename(
        Community_Acquired_Pneumonia_radiologically_confirmed = Final.Standard.of.Care.LRTD.related.diagnosis..choice.CAP...radiologically.confirmed.,
        Community_Acquired_Pneumonia_clinically_confirmed = Final.Standard.of.Care.LRTD.related.diagnosis..choice.CAP...clinically.confirmed..but.not.on.radiology..,
        Community_Acquired_Pneumonia_no_radiology_performed = Final.Standard.of.Care.LRTD.related.diagnosis..choice.CAP...no.radiology.performed.,
        Acute_bronchitis = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Acute.bronchitis.,
        Exacerbation_of_COPD = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Exacerbation.of.COPD.,
        Empyema_lung_abscess = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Empyema.lung.abscess.,
        LRTI_not_further_specified = Final.Standard.of.Care.LRTD.related.diagnosis..choice.LRTI...not.further.specified.,
        Congestive_heart_failure = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Congestive.heart.failure.,
        Non_infectious_process = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Non.infectious.process.,
        Non_LRTD_infection_related_diagnosis = Final.Standard.of.Care.LRTD.related.diagnosis..choice.Non.LRTD.infection.related.diagnosis.,
        Other_LRTI_specified = Other.LRTI.Specified,
        NYHA_Heart_failure = NYHA...Heart.Failure..nbsp.,
        CRB65_Score = CRB65.Score,
        NEWS2_Score = NEWS.2.Score,
        Respiratory_Disease_None = Respiratory.Disease..choice.None.,
        COPD = Respiratory.Disease..choice.COPD..Chronic.Obstructive.Pulmonary.Disease.Emphysema..,
        Asthma = Respiratory.Disease..choice.Asthma.,
        Bronchiectasis = Respiratory.Disease..choice.Bronchiectasis.,
        Pulmonary_Fibrosis_Interstitial_Lung_Disease = Respiratory.Disease..choice.Pulmonary.Fibrosis.Interstitial.Lung.Disease.,
        Respiratory_Disease_other = Respiratory.Disease..choice.Other.,
        Chronic_heart_disease_none = Chronic.Heart.Disease..choice.None.,
        Hypertension = Chronic.Heart.Disease..choice.Hypertension.,
        Atrial_Fibrillation = Chronic.Heart.Disease..choice.Atrial.Fibrillation.,
        Ischaemic_heart_disease = Chronic.Heart.Disease..choice.Ischaemic.heart.disease.,
        Heart_failure = Chronic.Heart.Disease..choice.Heart.failure.CCF.,
        Chronic_heart_disease_other = Chronic.Heart.Disease..choice.Other.,
        Chronic_Kidney_Disease = Chronic.Kidney.Disease..CKD..Mod.Severe..eGFR..30..Cr.265.umol.L..dialysis..transplantation..uremic.syndrome,
        Liver_disease = Liver.Disease.Mild...nbsp.cirrhosis.without.portal.HTN..chronic.hepatitis..Mod.Severe...nbsp.cirrhosis.with.portal.HTN.....variceal.bleeding,
        Diabetes = Diabetes,
        Cognitive_Impairment_Dementia_none = Cognitive.Impairment.Dementia..choice.None.,
        Dementia = Cognitive.Impairment.Dementia..choice.Dementia.,
        Cognitive_impairment = Cognitive.Impairment.Dementia..choice.Cognitive.Impairment.,
        CVA_Stroke = Cognitive.Impairment.Dementia..choice.CVA..stroke..,
        TIA_mini_stroke = Cognitive.Impairment.Dementia..choice.TIA..mini.stroke..,
        Hemiplegiahemiplegia_or_paraplegia = Hemiplegiahemiplegia.or.paraplegia,
        Peripheral_vascular_disease = Peripheral.Vascular.Disease.Intermittent.claudication..periph..arterial.bypass.for.insufficiency..gangrene..acute.arterial.insufficiency..untreated.aneurysm....6cm..nbsp.,
        Immunosuppressive_medication = Immunosuppressive.Medication.includes.oral.steroids..biologics..chemotherapy.,
        Immunodeficiency = Immunodeficiency.eg.SCID..hypogammaglobulinaemia..splenectomy.,
        Connective_tissue_disease = Connective.Tissue.Disease..SLE..polymyositis..mixed.nbsp.Connective.Tissue.Disease..polymyalgia.rheumatica..moderate.to.severe.Rheumatoid.Arthritis.,
        HIV_negative_or_not_tested = HIV.status..choice.Negative..no.HIV...or.not.tested.,
        HIV_positive = HIV.status..choice.HIV.,
        AIDS = HIV.status..choice.AIDS.,
        Solid_organ_cancer_malignancy = Solid.Organ.Cancer.Malignancy.Initially.treated.in.the.last.5.years.exclude.non.melanomatous.skin.cancers.and.in.situ.cervical.carcinoma,
        Haematological_malignancy_leukaemia_none = Haematological.Malignancy.Leukaemia...nbsp.CML..CLL..AML..ALL..Polycythaemia.Vera.Lymphoma...nbsp.NHL..Hodgkin.s..WaldenstrÃ.m..multiple.myeloma...choice.None.,
        Leukaemia = Haematological.Malignancy.Leukaemia...nbsp.CML..CLL..AML..ALL..Polycythaemia.Vera.Lymphoma...nbsp.NHL..Hodgkin.s..WaldenstrÃ.m..multiple.myeloma...choice.Leukaemia.,
        Lymphoma = Haematological.Malignancy.Leukaemia...nbsp.CML..CLL..AML..ALL..Polycythaemia.Vera.Lymphoma...nbsp.NHL..Hodgkin.s..WaldenstrÃ.m..multiple.myeloma...choice.Lymphoma.,
        Organ_transplantation = Organ.Transplantation,
        Pregnancy_post_partum = Pregnancy.Post.partum,
        Gastric_Duodenal_Ulcer_disease = Gastric.Duodenal.Ulcer.Disease.Patients.who.have.required.treatment.for.PUD.nbsp.,
        Rockwood_frailty_score = Rockwood.Frailty.Score,
        Radiology_result = Radiology.Result
    )
```

## Demographics Table
Age and gender for every individual

```{r}
dem = Vir %>%
  distinct(ID, .keep_all = TRUE)
dem = dem %>%
  select(ID,Gender,Age)
```


## Some discharge dates are missing where death date is present, need to replace NA with death date

If discharge date ISNT present, and death date IS present, then make discharge date the death date. THEN, calculate length of stay from (discharge date - admission date). 

```{r}

totalOutcomes$dischargeDate[is.na(totalOutcomes$dischargeDate)] <- totalOutcomes$deathDate[is.na(totalOutcomes$dischargeDate)]
```



## Calculate length of stay

```{r}
totalOutcomes <- within(totalOutcomes, lengthOfStay <- dischargeDate - admissionDate)
```

### Only keep positive lengths of stay
I think there are some issues with a handful of admission times, as they produce a negative length of stay. I've checked the original data and this issue lies with the original data source.

```{r}
totalOutcomes <- totalOutcomes[totalOutcomes$lengthOfStay >= 0,]
```



### Frequency plot length of stay

```{r}
ggplot(totalOutcomes, aes(lengthOfStay)) + 
  geom_histogram(binwidth=1,boundary=0, color="black",fill="blue")
```
```{r}
ggplot(data = totalOutcomes, aes(x = lengthOfStay)) + 
  geom_histogram(aes(y=cumsum(..count..)),binwidth=1, boundary=0, color="black",fill="blue")
```

### Create age breaks and labels, then convert to factor

```{r}
agebreaks <- c(5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100,105)
agelabels <- c("5-9","10-14","15-19","20-24","25-29","30-34","35-39","40,44","45-49","50-54","55-59","60-64","65-69","70-74","75-79","80-84","85-89","90-94","95-99","100-105")

setDT(dem)[, agegroups := cut (Age,
                               breaks = agebreaks,
                               right = FALSE,
                               labels = agelabels)]

dem$Population <- 1 # Each respondent is one person

dem$agegroups <- as.factor(dem$agegroups)

dem$Population <- ifelse(dem$Gender == "M", -1*dem$Population, dem$Population)
```

### Min, median and mean length of stay
```{r}
print(min(totalOutcomes$lengthOfStay, na.rm=T))
print(mean(totalOutcomes$lengthOfStay, na.rm=T))
print(median(totalOutcomes$lengthOfStay, na.rm=T))
```


### Create stacked pyramid plot to stratify for age and gender

```{r}
ggplot(data = dem, aes(x = agegroups, y=Population, fill = Gender)) +
  geom_bar(subset=(dem$Gender=="F"), stat="identity") +
  geom_bar(subset=(dem$Gender=="M"), stat="identity") +
  scale_y_continuous() + 
  coord_flip()
```

### Demographics of those that have died

- Find a subset of those that have died
- Present graph

```{r}
# Those that have died
deceasedSubset = subset(totalOutcomes, !is.na(totalOutcomes$deathDate))

# Semi-join for those that have died in total outcomes with the demographics table
deceasedDem = semi_join(dem, deceasedSubset, by = c("ID"="ID"))

ggplot(data = deceasedDem, aes(x = agegroups, y=Population, fill = Gender)) +
  scale_x_discrete(drop=FALSE) +
  geom_bar(subset=(deceasedDem$Gender=="F"), stat="identity") +
  geom_bar(subset=(deceasedDem$Gender=="M"), stat="identity") +
  scale_y_continuous() + 
  coord_flip()
```

### Find the demographics of those that went to ICU

```{r}
# Those that have died
ICU_subset = subset(totalOutcomes, !is.na(totalOutcomes$ITU_Start))

# Semi-join for those that have died in total outcomes with the demographics table
ICU_dem = semi_join(dem, ICU_subset, by = c("ID"="ID"))

ggplot(data = ICU_dem, aes(x = agegroups, y=Population, fill = Gender)) +
  scale_x_discrete(drop=FALSE) +
  geom_bar(subset=(ICU_dem$Gender=="F"), stat="identity") +
  geom_bar(subset=(ICU_dem$Gender=="M"), stat="identity") +
  scale_y_continuous() + 
  coord_flip()
```


### Rescale tables, add "Measure" column so that it can act as a factor, and combine tables

```{r}
BE$BE_val <- rescale(BE$BE_val)
BE = BE %>% select(ID,date,BE_val)
BE['Measure'] = 'BE'
BE = BE %>%
    rename ( 
        Numeric.Result = BE_val
    )

BNP$BNP_val <- rescale(BNP$BNP_val)
BNP = BNP %>% select(ID,date,BNP_val)
BNP['Measure'] = 'BNP'
BNP = BNP %>%
    rename ( 
        Numeric.Result = BNP_val
    )

CRP$CRP_val <- rescale(CRP$CRP_val)
CRP = CRP %>% select(ID,date,CRP_val)
CRP['Measure'] = 'CRP'
CRP = CRP %>%
    rename ( 
        Numeric.Result = CRP_val
    )

DDM$DDM_val <- rescale(DDM$DDM_val)
DDM = DDM %>% select(ID,date,DDM_val)
DDM['Measure'] = 'DDM'
DDM = DDM %>%
    rename ( 
        Numeric.Result = DDM_val
    )

eGFR$eGFR_val <- rescale(eGFR$eGFR_val)
eGFR = eGFR %>% select(ID,date,eGFR_val)
eGFR['Measure'] = 'eGFR'
eGFR = eGFR %>%
    rename ( 
        Numeric.Result = eGFR_val
    )

FER$FER_val <- rescale(FER$FER_val)
FER = FER %>% select(ID,date,FER_val)
FER['Measure'] = 'FER'
FER = FER %>%
    rename ( 
        Numeric.Result = FER_val
    )

fib$fib_val <- rescale(fib$fib_val)
fib = fib %>% select(ID,date,fib_val)
fib['Measure'] = 'fib'
fib = fib %>%
    rename ( 
        Numeric.Result = fib_val
    )

Glucose$Glucose_val <- rescale(Glucose$Glucose_val)
Glucose = Glucose %>% select(ID,date,Glucose_val)
Glucose['Measure'] = 'Glucose'
Glucose = Glucose %>%
    rename ( 
        Numeric.Result = Glucose_val
    )

HB$HB_val <- rescale(HB$HB_val)
HB = HB %>% select(ID,date,HB_val)
HB['Measure'] = 'HB'
HB = HB %>%
    rename ( 
        Numeric.Result = HB_val
    )

ClotAPTT$APTT_val <- rescale(ClotAPTT$APTT_val)
ClotAPTT = ClotAPTT %>% select(ID,date,APTT_val)
ClotAPTT['Measure'] = 'APTT'
ClotAPTT = ClotAPTT %>%
    rename ( 
        Numeric.Result = APTT_val
    )

ClotPT$PT_val <- rescale(ClotPT$PT_val)
ClotPT = ClotPT %>% select(ID,date,PT_val)
ClotPT['Measure'] = 'PT'
ClotPT = ClotPT %>%
    rename ( 
        Numeric.Result = PT_val
    )

CO2$CO2_val <- rescale(CO2$CO2_val)
CO2 = CO2 %>% select(ID,date,CO2_val)
CO2['Measure'] = 'CO2'
CO2 = CO2 %>%
    rename ( 
        Numeric.Result = CO2_val
    )

O2$O2_val <- rescale(O2$O2_val)
O2 = O2 %>% select(ID,date,O2_val)
O2['Measure'] = 'O2'
O2 = O2 %>%
    rename ( 
        Numeric.Result = O2_val
    )

FBCLymph$Lymphocytes <- rescale(FBCLymph$Lymphocytes)
FBCLymph = FBCLymph %>% select(ID,date,Lymphocytes)
FBCLymph['Measure'] = 'Lymphocytes'
FBCLymph = FBCLymph %>%
    rename ( 
        Numeric.Result = Lymphocytes
    )

FBCNeutr$Neutrophils <- rescale(FBCNeutr$Neutrophils)
FBCNeutr = FBCNeutr %>% select(ID,date,Neutrophils)
FBCNeutr['Measure'] = 'Neutrophils'
FBCNeutr = FBCNeutr %>%
    rename ( 
        Numeric.Result = Neutrophils
    )

FBCNLR$NLR_val <- rescale(FBCNLR$NLR_val)
FBCNLR = FBCNLR %>% select(ID,date,NLR_val)
FBCNLR['Measure'] = 'NLR'
FBCNLR = FBCNLR %>%
    rename ( 
        Numeric.Result = NLR_val
    )

FBCWCC$WCC <- rescale(FBCWCC$WCC)
FBCWCC = FBCWCC %>% select(ID,date,WCC)
FBCWCC['Measure'] = 'WCC'
FBCWCC = FBCWCC %>%
    rename ( 
        Numeric.Result = WCC
    )

HBA1c$HBA1c_val <- rescale(HBA1c$HBA1c_val)
HBA1c = HBA1c %>% select(ID,date,HBA1c_val)
HBA1c['Measure'] = 'HBA1c'
HBA1c = HBA1c %>%
    rename ( 
        Numeric.Result = HBA1c_val
    )

poctpH$poctpH_val <- rescale(poctpH$poctpH_val)
poctpH = poctpH %>% select(ID,date,poctpH_val)
poctpH['Measure'] = 'poctpH'
poctpH$date = as.Date(poctpH$date, format="%d/%m/%Y")
poctpH = poctpH %>%
    rename ( 
        Numeric.Result = poctpH_val
    )


poctLAC$poctLAC_val <- rescale(poctLAC$poctLAC_val)
poctLAC = poctLAC %>% select(ID,date,poctLAC_val)
poctLAC['Measure'] = 'poctLAC'
poctLAC = poctLAC %>%
    rename ( 
        Numeric.Result = poctLAC_val
    )

LDH$LDH_val <- rescale(LDH$LDH_val)
LDH = LDH %>% select(ID,date,LDH_val)
LDH['Measure'] = 'LDH'
LDH = LDH %>%
    rename ( 
        Numeric.Result = LDH_val
    )

PCT$PCT_val <- rescale(PCT$PCT_val)
PCT = PCT %>% select(ID,date,PCT_val)
PCT['Measure'] = 'PCT'
PCT = PCT %>%
    rename ( 
        Numeric.Result = PCT_val
    )

PLT$PLT_val <- rescale(PLT$PLT_val)
PLT = PLT %>% select(ID,date,PLT_val)
PLT['Measure'] = 'PLT'
PLT = PLT %>%
    rename ( 
        Numeric.Result = PLT_val
    )

trig$trig_val <- rescale(trig$trig_val)
trig = trig %>% select(ID,date,trig_val)
trig['Measure'] = 'trig'
trig = trig %>%
    rename ( 
        Numeric.Result = trig_val
    )

trop$trop_val <- rescale(trop$trop_val)
trop = trop %>% select(ID,date,trop_val)
trop['Measure'] = 'trop'
trop = trop %>%
    rename ( 
        Numeric.Result = trop_val
    )


```

### Merge tables

```{r}
total <- rbind(BE,BNP,CRP,DDM,eGFR,FER,fib,Glucose,HB,ClotAPTT,ClotPT,CO2,O2,FBCLymph,FBCNeutr,FBCNLR,FBCWCC,HBA1c,poctpH,poctLAC,LDH,PCT,PLT,trig,trop)
total$Measure <- factor(total$Measure, levels = c("BNP","LDH","HBA1c","trig","trop","DDM","FER","PCT","fib","Glucose","PT","APTT","PLT","CRP","eGFR","poctLAC","poctpH","O2","CO2","WCC","Lymphocytes","Neutrophils","NLR","HB","BE"))
```

### Setting day of admission as day 0, and calculating days since admission

Still need to add multiple admissions

```{r}
total$firstBookedIn <- 0
for (i in 1:nrow(total)){
  total$firstBookedIn[i] <- (total$date[which(total$ID==total$ID[i])][1])
}
total$firstBookedIn <- as.Date(total$firstBookedIn,origin = "1970-01-01")
total$Days = as.integer(total$date - total$firstBookedIn)



```
### Plotting the lab values of all patients on day of admission

```{r}
total_day1 <- subset(total, Days == 0)
total_day1$date <- as.Date(total_day1$date, format="%d/%m/%Y")

ggplot(total_day1, aes(x=Numeric.Result, y=Measure)) +
  scale_y_discrete(guide = guide_axis(n.dodge=2), drop=FALSE) +
  geom_boxplot() + 
  coord_flip()
```

### Subsetting those lab values from covid positive date

```{r}
total_positiveDay <- semi_join(total,CovidCT, by = c("ID" = "ID", "date" = "date"))

ggplot(total_positiveDay, aes(x=Numeric.Result, y=Measure)) +
  scale_y_discrete(guide = guide_axis(n.dodge=2), drop=FALSE) +
  geom_boxplot() + 
  coord_flip()
```

```{r}
total_ICU <- semi_join(total,subset(totalOutcomes,!is.na(totalOutcomes$ITU_Start)), by = c("ID" = "ID") )
total_ICU <- subset(total_ICU, Days == 0)

ggplot(total_ICU, aes(x=Numeric.Result, y=Measure)) +
  scale_y_discrete(guide = guide_axis(n.dodge=2), drop=FALSE) +
  geom_boxplot() + 
  coord_flip()
```
### Variable boxplots
For each:
* Transform to ~ normal distribution
* Rescale
For each, show:
* Results on day of admission
* Results on day of positive test
* Results on day of ICU admission
* Display clinical thresholds alongside. 

### BE

```{r}
# Store range of BE before rescale
# Reference range is 22-29

BE <- read.csv(file("BE.csv"))
BE$Date.Booked.In = as.Date(BE$Date.Booked.In, format="%d/%m/%Y")
BE = BE %>% 
  rename(
    date = Date.Booked.In,
  )
BE = BE %>%
  rename(
    BE_val = Numeric.Result
  )

BE_range = range(BE$BE_val, na.rm=TRUE)
BE_bottom_ref = 22
BE_top_ref = 29

BE$BE_val <- Winsorize(BE$BE_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

BE$BE_val <- rescale(BE$BE_val, to=c(0,1), from = BE_range)
BE_bottom_ref = rescale(BE_bottom_ref, to=c(0,1), from = BE_range)
BE_top_ref = rescale(BE_top_ref, to=c(0,1), from = BE_range)

BE = BE %>% select(ID,date,BE_val)
BE_day1 <- semi_join(BE,total_day1, by = c("ID" = "ID", "date" = "date"))
BE_positive <- semi_join(BE,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
BE_ICU <- semi_join(BE,total_ICU, by = c("ID" = "ID", "date" = "date"))

BE$Label <- "All values"
BE_day1$Label <- "Values on admission"
BE_positive$Label <- "Values on COVID + day"
BE_ICU$Label <- "Values for ICU patients"

BE <- rbind(BE,BE_day1,BE_positive,BE_ICU)

ggplot() +
  ggtitle("BE distribution") +
  labs(subtitle="Reference range = 22-29") + 
  geom_boxplot(data = BE, aes(x=BE_val,y=Label)) + 
  coord_flip() + 
  geom_vline(xintercept=BE_bottom_ref,colour="red") +
  geom_vline(xintercept=BE_top_ref,colour="red")
```

BNP has outliers and a positive skew - log transformation

```{r}
# Men under 70: <100pg/ml, Women under 70: <150 pg/ml, All 70yr and over: <300 pg/ml

BNP <- read.csv(file("BNP.csv"))
BNP$Date.Booked.In = as.Date(BNP$Date.Booked.In, format="%d/%m/%Y")
BNP = BNP %>% 
  rename(
    date = Date.Booked.In,
  )
BNP = BNP %>%
  rename(
    BNP_val = Numeric.Result
  )

BNP$BNP_val <- log10(BNP$BNP_val)

BNP_range = range(BNP$BNP_val, na.rm=TRUE)
BNP_bottom_ref = log10(100)
BNP_middle_ref = log10(150)
BNP_top_ref = log10(300)

BNP$BNP_val <- Winsorize(BNP$BNP_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

BNP$BNP_val <- rescale(BNP$BNP_val, to=c(0,1), from = BNP_range)
BNP_bottom_ref = rescale(BNP_bottom_ref, to=c(0,1), from = BNP_range)
BNP_middle_ref = rescale(BNP_middle_ref, to=c(0,1), from = BNP_range)
BNP_top_ref = rescale(BNP_top_ref, to=c(0,1), from = BNP_range)

BNP = BNP %>% select(ID,date,BNP_val)
BNP_day1 <- semi_join(BNP,total_day1, by = c("ID" = "ID", "date" = "date"))
BNP_positive <- semi_join(BNP,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
BNP_ICU <- semi_join(BNP,total_ICU, by = c("ID" = "ID", "date" = "date"))

BNP$Label <- "All values"
BNP_day1$Label <- "Values on admission"
BNP_positive$Label <- "Values on COVID + day"
BNP_ICU$Label <- "Values for ICU patients"

BNP <- rbind(BNP,BNP_day1,BNP_positive,BNP_ICU)

ggplot() +
  ggtitle("BNP distribution") +
  labs(subtitle="Men under 70: <100pg/ml, Women under 70: <150 pg/ml, All 70yr and over: <300 pg/ml") + 
  geom_boxplot(data = BNP, aes(x=BNP_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=BNP_bottom_ref,colour="red") +
  geom_vline(xintercept=BNP_middle_ref,colour="red") + 
  geom_vline(xintercept=BNP_top_ref,colour="red") 


```


```{r}
# CRP Reference range < 6mg/L

CRP <- read.csv(file("CRP.csv"))
CRP$Date.Booked.In = as.Date(CRP$Date.Booked.In, format="%d/%m/%Y")
CRP = CRP %>% 
  rename(
    date = Date.Booked.In,
  )
CRP = CRP %>%
  rename(
    CRP_val = Numeric.Result
  )

CRP$CRP_val <- (CRP$CRP_val)^(1/3)

CRP_range = range(CRP$CRP_val, na.rm=TRUE)
CRP_bottom_ref = 6^(1/3)

CRP$CRP_val <- Winsorize(CRP$CRP_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

CRP$CRP_val <- rescale(CRP$CRP_val, to=c(0,1), from = CRP_range)
CRP_bottom_ref = rescale(CRP_bottom_ref, to=c(0,1), from = CRP_range)


CRP = CRP %>% select(ID,date,CRP_val)
CRP_day1 <- semi_join(CRP,total_day1, by = c("ID" = "ID", "date" = "date"))
CRP_positive <- semi_join(CRP,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
CRP_ICU <- semi_join(CRP,total_ICU, by = c("ID" = "ID", "date" = "date"))

CRP$Label <- "All values"
CRP_day1$Label <- "Values on admission"
CRP_positive$Label <- "Values on COVID + day"
CRP_ICU$Label <- "Values for ICU patients"

CRP <- rbind(CRP,CRP_day1,CRP_positive,CRP_ICU)

ggplot() +
  ggtitle("CRP distribution") +
  labs(subtitle="Reference range = < 6 mg/L") + 
  geom_boxplot(data = CRP, aes(x=CRP_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=CRP_bottom_ref,colour="red")

```


```{r}
# Reference range (ng/ml) = Age < 60: <500, Age 61-70: <600, Age 71-80: <700, Age 81-90: <800, Age > 90: <900

DDM <- read.csv(file("DDM.csv"))
DDM$Date.Booked.In = as.Date(DDM$Date.Booked.In, format="%d/%m/%Y")
DDM = DDM %>% 
  rename(
    date = Date.Booked.In,
  )
DDM = DDM %>%
  rename(
    DDM_val = Numeric.Result
  )

DDM$DDM_val <- log10(DDM$DDM_val)

DDM_range = range(DDM$DDM_val, na.rm=TRUE)
DDM_ref_1 = log10(500)
DDM_ref_2 = log10(600)
DDM_ref_3 = log10(700)
DDM_ref_4 = log10(800)
DDM_ref_5 = log10(900)



DDM$DDM_val <- Winsorize(DDM$DDM_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

DDM$DDM_val <- rescale(DDM$DDM_val, to=c(0,1), from = DDM_range)
DDM_ref_1 = rescale(DDM_ref_1, to=c(0,1), from = DDM_range)
DDM_ref_2 = rescale(DDM_ref_2, to=c(0,1), from = DDM_range)
DDM_ref_3 = rescale(DDM_ref_3, to=c(0,1), from = DDM_range)
DDM_ref_4 = rescale(DDM_ref_4, to=c(0,1), from = DDM_range)
DDM_ref_5 = rescale(DDM_ref_5, to=c(0,1), from = DDM_range)


DDM = DDM %>% select(ID,date,DDM_val)
DDM_day1 <- semi_join(DDM,total_day1, by = c("ID" = "ID", "date" = "date"))
DDM_positive <- semi_join(DDM,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
DDM_ICU <- semi_join(DDM,total_ICU, by = c("ID" = "ID", "date" = "date"))

DDM$Label <- "All values"
DDM_day1$Label <- "Values on admission"
DDM_positive$Label <- "Values on COVID + day"
DDM_ICU$Label <- "Values for ICU patients"

DDM <- rbind(DDM,DDM_day1,DDM_positive,DDM_ICU)

ggplot() +
  ggtitle("DDM distribution") +
  labs(subtitle="Men under 70: <100pg/ml, Women under 70: <150 pg/ml, All 70yr and over: <300 pg/ml") + 
  geom_boxplot(data = DDM, aes(x=DDM_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=DDM_ref_1,colour="red") +
  geom_vline(xintercept=DDM_ref_2,colour="red") +
  geom_vline(xintercept=DDM_ref_3,colour="red") +
  geom_vline(xintercept=DDM_ref_4,colour="red") +
  geom_vline(xintercept=DDM_ref_5,colour="red") 

```

```{r}
# Reference range =  >90 
# NEED TO ADD VALUES "more than 90" - refer to excel document

eGFR <- read.csv(file("eGFR.csv"))
eGFR$Date.Booked.In = as.Date(eGFR$Date.Booked.In, format="%d/%m/%Y")
eGFR = eGFR %>% 
  rename(
    date = Date.Booked.In,
  )
eGFR = eGFR %>%
  rename(
    eGFR_val = Numeric.Result
  )

eGFR_range = range(eGFR$eGFR_val, na.rm=TRUE)
eGFR_ref = 90

eGFR$eGFR_val <- Winsorize(eGFR$eGFR_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

eGFR$eGFR_val <- rescale(eGFR$eGFR_val, to=c(0,1), from = eGFR_range)
eGFR_ref = rescale(eGFR_ref, to=c(0,1), from = eGFR_range)

eGFR = eGFR %>% select(ID,date,eGFR_val)
eGFR_day1 <- semi_join(eGFR,total_day1, by = c("ID" = "ID", "date" = "date"))
eGFR_positive <- semi_join(eGFR,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
eGFR_ICU <- semi_join(eGFR,total_ICU, by = c("ID" = "ID", "date" = "date"))

eGFR$Label <- "All values"
eGFR_day1$Label <- "Values on admission"
eGFR_positive$Label <- "Values on COVID + day"
eGFR_ICU$Label <- "Values for ICU patients"

eGFR <- rbind(eGFR,eGFR_day1,eGFR_positive,eGFR_ICU)

ggplot() +
  ggtitle("eGFR distribution") +
  labs(subtitle="Reference range = >90") + 
  geom_boxplot(data = eGFR, aes(x=eGFR_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=eGFR_ref,colour="red") 

```


```{r}
# Reference range Male: 33-490, Female(0-44): 15-445, Female(45+yrs): 30-470


FER <- read.csv(file("FER.csv"))
FER$Date.Booked.In = as.Date(FER$Date.Booked.In, format="%d/%m/%Y")
FER = FER %>% 
  rename(
    date = Date.Booked.In,
  )
FER = FER %>%
  rename(
    FER_val = Numeric.Result
  )

FER$FER_val <- log10(FER$FER_val)

FER_range = range(FER$FER_val, na.rm=TRUE)
FER_ref_1 = log10(15)
FER_ref_2 = log10(35)
FER_ref_3 = log10(445)
FER_ref_4 = log10(470)
FER_ref_5 = log10(490)


FER$FER_val <- Winsorize(FER$FER_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

FER$FER_val <- rescale(FER$FER_val, to=c(0,1), from = FER_range)
FER_ref_1 = rescale(FER_ref_1, to=c(0,1), from = FER_range)
FER_ref_2 = rescale(FER_ref_2, to=c(0,1), from = FER_range)
FER_ref_3 = rescale(FER_ref_3, to=c(0,1), from = FER_range)
FER_ref_4 = rescale(FER_ref_4, to=c(0,1), from = FER_range)
FER_ref_5 = rescale(FER_ref_5, to=c(0,1), from = FER_range)


FER = FER %>% select(ID,date,FER_val)
FER_day1 <- semi_join(FER,total_day1, by = c("ID" = "ID", "date" = "date"))
FER_positive <- semi_join(FER,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
FER_ICU <- semi_join(FER,total_ICU, by = c("ID" = "ID", "date" = "date"))

FER$Label <- "All values"
FER_day1$Label <- "Values on admission"
FER_positive$Label <- "Values on COVID + day"
FER_ICU$Label <- "Values for ICU patients"

FER <- rbind(FER,FER_day1,FER_positive,FER_ICU)

ggplot() +
  ggtitle("FER distribution") +
  labs(subtitle="Reference range Male: 33-490, Female(0-44): 15-445, Female(45+yrs): 30-470") + 
  geom_boxplot(data = FER, aes(x=FER_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=FER_ref_1,colour="green") +
  geom_vline(xintercept=FER_ref_2,colour="blue") +
  geom_vline(xintercept=FER_ref_3,colour="green") +
  geom_vline(xintercept=FER_ref_4,colour="red") +
  geom_vline(xintercept=FER_ref_5,colour="blue") 

```


```{r}

# Reference range = 1.8-4.0 g/L

fib <- read.csv(file("fib.csv"))
fib$Date.Booked.In = as.Date(fib$Date.Booked.In, format="%d/%m/%Y")
fib = fib %>% 
  rename(
    date = Date.Booked.In,
  )
fib = fib %>%
  rename(
    fib_val = Numeric.Result
  )

fib_range = range(fib$fib_val, na.rm=TRUE)
fib_bottom_ref = 1.8
fib_top_ref = 4

fib$fib_val <- Winsorize(fib$fib_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

fib$fib_val <- rescale(fib$fib_val, to=c(0,1), from = fib_range)
fib_bottom_ref = rescale(fib_bottom_ref, to=c(0,1), from = fib_range)
fib_top_ref = rescale(fib_top_ref, to=c(0,1), from = fib_range)

fib = fib %>% select(ID,date,fib_val)
fib_day1 <- semi_join(fib,total_day1, by = c("ID" = "ID", "date" = "date"))
fib_positive <- semi_join(fib,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
fib_ICU <- semi_join(fib,total_ICU, by = c("ID" = "ID", "date" = "date"))

fib$Label <- "All values"
fib_day1$Label <- "Values on admission"
fib_positive$Label <- "Values on COVID + day"
fib_ICU$Label <- "Values for ICU patients"

fib <- rbind(fib,fib_day1,fib_positive,fib_ICU)

ggplot() +
  ggtitle("fib distribution") +
  labs(subtitle="Reference range = 1.8-4.0 g/L") + 
  geom_boxplot(data = fib, aes(x=fib_val,y=Label)) + 
  coord_flip() + 
  geom_vline(xintercept=fib_bottom_ref,colour="red") +
  geom_vline(xintercept=fib_top_ref,colour="red")

```


```{r}
# Reference range = Fasting: 3.0-6.0 mmol/L, Non-fasting: 3.0-7.8 mmol/L

Glucose <- read.csv(file("Glucose.csv"))
Glucose$Date.Booked.In = as.Date(Glucose$Date.Booked.In, format="%d/%m/%Y")
Glucose = Glucose %>% 
  rename(
    date = Date.Booked.In,
  )
Glucose = Glucose %>%
  rename(
    Glucose_val = Numeric.Result
  )

Glucose$Glucose_val <- log10(Glucose$Glucose_val)

Glucose_range = range(Glucose$Glucose_val, na.rm=TRUE)
Glucose_bottom_ref = log10(3)
Glucose_middle_ref = log10(6)
Glucose_top_ref = log10(7.8)

Glucose$Glucose_val <- Winsorize(Glucose$Glucose_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

Glucose$Glucose_val <- rescale(Glucose$Glucose_val, to=c(0,1), from = Glucose_range)
Glucose_bottom_ref = rescale(Glucose_bottom_ref, to=c(0,1), from = Glucose_range)
Glucose_middle_ref = rescale(Glucose_middle_ref, to=c(0,1), from = Glucose_range)
Glucose_top_ref = rescale(Glucose_top_ref, to=c(0,1), from = Glucose_range)

Glucose = Glucose %>% select(ID,date,Glucose_val)
Glucose_day1 <- semi_join(Glucose,total_day1, by = c("ID" = "ID", "date" = "date"))
Glucose_positive <- semi_join(Glucose,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
Glucose_ICU <- semi_join(Glucose,total_ICU, by = c("ID" = "ID", "date" = "date"))

Glucose$Label <- "All values"
Glucose_day1$Label <- "Values on admission"
Glucose_positive$Label <- "Values on COVID + day"
Glucose_ICU$Label <- "Values for ICU patients"

Glucose <- rbind(Glucose,Glucose_day1,Glucose_positive,Glucose_ICU)

ggplot() +
  ggtitle("Glucose distribution") +
  labs(subtitle="Reference range = Fasting: 3.0-6.0 mmol/L, Non-fasting: 3.0-7.8 mmol/L") + 
  geom_boxplot(data = Glucose, aes(x=Glucose_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=Glucose_bottom_ref,colour="red") +
  geom_vline(xintercept=Glucose_middle_ref,colour="red") + 
  geom_vline(xintercept=Glucose_top_ref,colour="red") 

```

```{r}
# Reference range = Male 130-170 g/L, Female 120-150 g/L

HB <- read.csv(file("HB.csv"))
HB$Date.Booked.In = as.Date(HB$Date.Booked.In, format="%d/%m/%Y")
HB = HB %>% 
  rename(
    date = Date.Booked.In,
  )
HB = HB %>%
  rename(
    HB_val = Numeric.Result
  )


HB_range = range(HB$HB_val, na.rm=TRUE)
HB_ref_1 = (120)
HB_ref_2 = (130)
HB_ref_3 = (150)
HB_ref_4 = (170)


HB$HB_val <- Winsorize(HB$HB_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

HB$HB_val <- rescale(HB$HB_val, to=c(0,1), from = HB_range)
HB_ref_1 = rescale(HB_ref_1, to=c(0,1), from = HB_range)
HB_ref_2 = rescale(HB_ref_2, to=c(0,1), from = HB_range)
HB_ref_3 = rescale(HB_ref_3, to=c(0,1), from = HB_range)
HB_ref_4 = rescale(HB_ref_4, to=c(0,1), from = HB_range)


HB = HB %>% select(ID,date,HB_val)
HB_day1 <- semi_join(HB,total_day1, by = c("ID" = "ID", "date" = "date"))
HB_positive <- semi_join(HB,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
HB_ICU <- semi_join(HB,total_ICU, by = c("ID" = "ID", "date" = "date"))

HB$Label <- "All values"
HB_day1$Label <- "Values on admission"
HB_positive$Label <- "Values on COVID + day"
HB_ICU$Label <- "Values for ICU patients"

HB <- rbind(HB,HB_day1,HB_positive,HB_ICU)

ggplot() +
  ggtitle("HB distribution") +
  labs(subtitle="Reference range = Male 130-170 g/L, Female 120-150 g/L") + 
  geom_boxplot(data = HB, aes(x=HB_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=HB_ref_1,colour="blue") +
  geom_vline(xintercept=HB_ref_2,colour="green") +
  geom_vline(xintercept=HB_ref_3,colour="blue") +
  geom_vline(xintercept=HB_ref_4,colour="green") 

```


```{r}
# Reference range = 21-33 seconds

Clot <- read.csv(file("Clot.csv"))
Clot$Date.Booked.In = as.Date(Clot$Date.Booked.In, format="%d/%m/%Y")
Clot = Clot %>% 
  rename(
    date = Date.Booked.In,
  )

ClotAPTT = Clot %>% select(ID,date,APTT)
ClotAPTT = ClotAPTT %>% 
  rename(
    APTT_val = APTT,
  )

ClotAPTT$APTT_val <- log10(ClotAPTT$APTT_val)

ClotAPTT_range = range(ClotAPTT$APTT_val, na.rm=TRUE)
ClotAPTT_ref_1 = log10(21)
ClotAPTT_ref_2 = log10(33)


ClotAPTT$APTT_val <- Winsorize(ClotAPTT$APTT_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

ClotAPTT$APTT_val <- rescale(ClotAPTT$APTT_val, to=c(0,1), from = ClotAPTT_range)
ClotAPTT_ref_1 = rescale(ClotAPTT_ref_1, to=c(0,1), from = ClotAPTT_range)
ClotAPTT_ref_2 = rescale(ClotAPTT_ref_2, to=c(0,1), from = ClotAPTT_range)



ClotAPTT = ClotAPTT %>% select(ID,date,APTT_val)
ClotAPTT_day1 <- semi_join(ClotAPTT,total_day1, by = c("ID" = "ID", "date" = "date"))
ClotAPTT_positive <- semi_join(ClotAPTT,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
ClotAPTT_ICU <- semi_join(ClotAPTT,total_ICU, by = c("ID" = "ID", "date" = "date"))

ClotAPTT$Label <- "All values"
ClotAPTT_day1$Label <- "Values on admission"
ClotAPTT_positive$Label <- "Values on COVID + day"
ClotAPTT_ICU$Label <- "Values for ICU patients"

ClotAPTT <- rbind(ClotAPTT,ClotAPTT_day1,ClotAPTT_positive,ClotAPTT_ICU)

ggplot() +
  ggtitle("ClotAPTT distribution") +
  labs(subtitle="Reference range = 21-33 seconds") + 
  geom_boxplot(data = ClotAPTT, aes(x=APTT_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=ClotAPTT_ref_1,colour="red") +
  geom_vline(xintercept=ClotAPTT_ref_2,colour="red") 

```


```{r}
# Reference range = 9.5-13 seconds

Clot <- read.csv(file("Clot.csv"))
Clot$Date.Booked.In = as.Date(Clot$Date.Booked.In, format="%d/%m/%Y")
Clot = Clot %>% 
  rename(
    date = Date.Booked.In,
  )

ClotPT = Clot %>% select(ID,date,PT)
ClotPT = ClotPT %>% 
  rename(
    PT_val = PT,
  )

ClotPT$PT_val <- log10(ClotPT$PT_val)

ClotPT_range = range(ClotPT$PT_val, na.rm=TRUE)
ClotPT_ref_1 = log10(9.5)
ClotPT_ref_2 = log10(13)


ClotPT$PT_val <- Winsorize(ClotPT$PT_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

ClotPT$PT_val <- rescale(ClotPT$PT_val, to=c(0,1), from = ClotPT_range)
ClotPT_ref_1 = rescale(ClotPT_ref_1, to=c(0,1), from = ClotPT_range)
ClotPT_ref_2 = rescale(ClotPT_ref_2, to=c(0,1), from = ClotPT_range)



ClotPT = ClotPT %>% select(ID,date,PT_val)
ClotPT_day1 <- semi_join(ClotPT,total_day1, by = c("ID" = "ID", "date" = "date"))
ClotPT_positive <- semi_join(ClotPT,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
ClotPT_ICU <- semi_join(ClotPT,total_ICU, by = c("ID" = "ID", "date" = "date"))

ClotPT$Label <- "All values"
ClotPT_day1$Label <- "Values on admission"
ClotPT_positive$Label <- "Values on COVID + day"
ClotPT_ICU$Label <- "Values for ICU patients"

ClotPT <- rbind(ClotPT,ClotPT_day1,ClotPT_positive,ClotPT_ICU)

ggplot() +
  ggtitle("ClotPT distribution") +
  labs(subtitle="Reference range = 9.5-13 seconds") + 
  geom_boxplot(data = ClotPT, aes(x=PT_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=ClotPT_ref_1,colour="red") +
  geom_vline(xintercept=ClotPT_ref_2,colour="red") 

```


```{r}
# Reference range = 4.6-6.4 seconds

poctO2 <- read.csv(file("poctO2.csv"))

CO2 <- poctO2 %>%
  filter(Test.Desc == "Arterial pCO2")
#Format date
CO2$Date.of.Specimen = as.Date(CO2$Date.of.Specimen, format="%d/%m/%Y")
CO2 = CO2 %>% 
  rename(
    date = Date.of.Specimen,
  )
CO2 = CO2 %>% 
  rename(
    time = Time.of.Specimen,
  )
CO2 = CO2 %>% 
  rename(
    CO2_val = Numeric.Result,
  )
#Combine date and time
CO2$dateTime = as.POSIXct(paste(CO2$date, CO2$time), format="%Y-%m-%d %H:%M:%S")

CO2$CO2_val <- log10(CO2$CO2_val)

CO2_range = range(CO2$CO2_val, na.rm=TRUE)
CO2_ref_1 = log10(4.6)
CO2_ref_2 = log10(6.4)


CO2$CO2_val <- Winsorize(CO2$CO2_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

CO2$CO2_val <- rescale(CO2$CO2_val, to=c(0,1), from = CO2_range)
CO2_ref_1 = rescale(CO2_ref_1, to=c(0,1), from = CO2_range)
CO2_ref_2 = rescale(CO2_ref_2, to=c(0,1), from = CO2_range)



CO2 = CO2 %>% select(ID,date,CO2_val)
CO2_day1 <- semi_join(CO2,total_day1, by = c("ID" = "ID", "date" = "date"))
CO2_positive <- semi_join(CO2,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
CO2_ICU <- semi_join(CO2,total_ICU, by = c("ID" = "ID", "date" = "date"))

CO2$Label <- "All values"
CO2_day1$Label <- "Values on admission"
CO2_positive$Label <- "Values on COVID + day"
CO2_ICU$Label <- "Values for ICU patients"

CO2 <- rbind(CO2,CO2_day1,CO2_positive,CO2_ICU)

ggplot() +
  ggtitle("CO2 distribution") +
  labs(subtitle="Reference range = 4.6-6.4 seconds") + 
  geom_boxplot(data = CO2, aes(x=CO2_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=CO2_ref_1,colour="red") +
  geom_vline(xintercept=CO2_ref_2,colour="red") 


```

```{r}
# Reference range = 11.0-14.4 seconds

O2 <- poctO2 %>%
  filter(Test.Desc == "Arterial pO2")
O2$Date.of.Specimen = as.Date(O2$Date.of.Specimen, format="%d/%m/%Y")
O2 = O2 %>% 
  rename(
    date = Date.of.Specimen,
  )
O2 = O2 %>% 
  rename(
    time = Time.of.Specimen,
  )
O2 = O2 %>% 
  rename(
    O2_val = Numeric.Result,
  )
#Combine date and time
O2$dateTime = as.POSIXct(paste(O2$date, O2$time), format="%Y-%m-%d %H:%M:%S")

O2$O2_val <- log10(O2$O2_val)

O2_range = range(O2$O2_val, na.rm=TRUE)
O2_ref_1 = log10(11)
O2_ref_2 = log10(14.4)


O2$O2_val <- Winsorize(O2$O2_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

O2$O2_val <- rescale(O2$O2_val, to=c(0,1), from = O2_range)
O2_ref_1 = rescale(O2_ref_1, to=c(0,1), from = O2_range)
O2_ref_2 = rescale(O2_ref_2, to=c(0,1), from = O2_range)



O2 = O2 %>% select(ID,date,O2_val)
O2_day1 <- semi_join(O2,total_day1, by = c("ID" = "ID", "date" = "date"))
O2_positive <- semi_join(O2,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
O2_ICU <- semi_join(O2,total_ICU, by = c("ID" = "ID", "date" = "date"))

O2$Label <- "All values"
O2_day1$Label <- "Values on admission"
O2_positive$Label <- "Values on COVID + day"
O2_ICU$Label <- "Values for ICU patients"

O2 <- rbind(O2,O2_day1,O2_positive,O2_ICU)

ggplot() +
  ggtitle("O2 distribution") +
  labs(subtitle="Reference range = 11.0-14.4 seconds") + 
  geom_boxplot(data = O2, aes(x=O2_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=O2_ref_1,colour="red") +
  geom_vline(xintercept=O2_ref_2,colour="red") 



```

```{r}
# Reference range =  1.5-4.5 10^9/L

FBC <- read.csv(file("FBC.csv"))
FBC$Date.Booked.In = as.Date(FBC$Date.Booked.In, format="%d/%m/%Y")
FBC = FBC %>% 
  rename(
    date = Date.Booked.In,
  )

FBCLymph = FBC %>% select(ID,date,Result.Lymphocytes)
FBCLymph = FBCLymph %>% 
  rename(
    Lymphocytes = Result.Lymphocytes,
  )

FBCLymph$Lymphocytes <- log10(FBCLymph$Lymphocytes)

FBCLymph_range = range(FBCLymph$Lymphocytes, na.rm=TRUE)
FBCLymph_ref_1 = log10(1.5)
FBCLymph_ref_2 = log10(4.5)


FBCLymph$Lymphocytes <- Winsorize(FBCLymph$Lymphocytes, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

FBCLymph$Lymphocytes <- rescale(FBCLymph$Lymphocytes, to=c(0,1), from = FBCLymph_range)
FBCLymph_ref_1 = rescale(FBCLymph_ref_1, to=c(0,1), from = FBCLymph_range)
FBCLymph_ref_2 = rescale(FBCLymph_ref_2, to=c(0,1), from = FBCLymph_range)



FBCLymph = FBCLymph %>% select(ID,date,Lymphocytes)
FBCLymph_day1 <- semi_join(FBCLymph,total_day1, by = c("ID" = "ID", "date" = "date"))
FBCLymph_positive <- semi_join(FBCLymph,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
FBCLymph_ICU <- semi_join(FBCLymph,total_ICU, by = c("ID" = "ID", "date" = "date"))

FBCLymph$Label <- "All values"
FBCLymph_day1$Label <- "Values on admission"
FBCLymph_positive$Label <- "Values on COVID + day"
FBCLymph_ICU$Label <- "Values for ICU patients"

FBCLymph <- rbind(FBCLymph,FBCLymph_day1,FBCLymph_positive,FBCLymph_ICU)

ggplot() +
  ggtitle("FBC_Lymph distribution") +
  labs(subtitle="Reference range =  1.5-4.5 10^9/L") + 
  geom_boxplot(data = FBCLymph, aes(x=Lymphocytes, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=FBCLymph_ref_1,colour="red") +
  geom_vline(xintercept=FBCLymph_ref_2,colour="red") 


```


```{r}
# Reference range = 2.0-7.5 10^9/L

FBC <- read.csv(file("FBC.csv"))
FBC$Date.Booked.In = as.Date(FBC$Date.Booked.In, format="%d/%m/%Y")
FBC = FBC %>% 
  rename(
    date = Date.Booked.In,
  )

FBCNeutr = FBC %>% select(ID,date,Result.Neutrophils)
FBCNeutr = FBCNeutr %>% 
  rename(
    Neutrophils = Result.Neutrophils,
  )

FBCNeutr$Neutrophils <- (FBCNeutr$Neutrophils)^(1/3)

FBCNeutr_range = range(FBCNeutr$Neutrophils, na.rm=TRUE)
FBCNeutr_ref_1 = (2)^(1/3)
FBCNeutr_ref_2 = (7.5)^(1/3)


FBCNeutr$Neutrophils <- Winsorize(FBCNeutr$Neutrophils, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

FBCNeutr$Neutrophils <- rescale(FBCNeutr$Neutrophils, to=c(0,1), from = FBCNeutr_range)
FBCNeutr_ref_1 = rescale(FBCNeutr_ref_1, to=c(0,1), from = FBCNeutr_range)
FBCNeutr_ref_2 = rescale(FBCNeutr_ref_2, to=c(0,1), from = FBCNeutr_range)



FBCNeutr = FBCNeutr %>% select(ID,date,Neutrophils)
FBCNeutr_day1 <- semi_join(FBCNeutr,total_day1, by = c("ID" = "ID", "date" = "date"))
FBCNeutr_positive <- semi_join(FBCNeutr,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
FBCNeutr_ICU <- semi_join(FBCNeutr,total_ICU, by = c("ID" = "ID", "date" = "date"))

FBCNeutr$Label <- "All values"
FBCNeutr_day1$Label <- "Values on admission"
FBCNeutr_positive$Label <- "Values on COVID + day"
FBCNeutr_ICU$Label <- "Values for ICU patients"

FBCNeutr <- rbind(FBCNeutr,FBCNeutr_day1,FBCNeutr_positive,FBCNeutr_ICU)

ggplot() +
  ggtitle("FBCNeutr distribution") +
  labs(subtitle="Reference range = 2.0-7.5 10^9/L") + 
  geom_boxplot(data = FBCNeutr, aes(x=Neutrophils, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=FBCNeutr_ref_1,colour="red") +
  geom_vline(xintercept=FBCNeutr_ref_2,colour="red") 

```

```{r}
# Reference range = 0.78 and 3.53

FBC <- read.csv(file("FBC.csv"))
FBC$Date.Booked.In = as.Date(FBC$Date.Booked.In, format="%d/%m/%Y")
FBC = FBC %>% 
  rename(
    date = Date.Booked.In,
  )

FBCNLR = FBC %>% select(ID,date,NLR)
FBCNLR = FBCNLR %>% 
  rename(
    NLR_val = NLR,
  )

FBCNLR$NLR_val <- log10(FBCNLR$NLR_val)

FBCNLR_range = range(FBCNLR$NLR_val, na.rm=TRUE)
FBCNLR_ref_1 = log10(0.78)
FBCNLR_ref_2 = log10(3.53)


FBCNLR$NLR_val <- Winsorize(FBCNLR$NLR_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

FBCNLR$NLR_val <- rescale(FBCNLR$NLR_val, to=c(0,1), from = FBCNLR_range)
FBCNLR_ref_1 = rescale(FBCNLR_ref_1, to=c(0,1), from = FBCNLR_range)
FBCNLR_ref_2 = rescale(FBCNLR_ref_2, to=c(0,1), from = FBCNLR_range)



FBCNLR = FBCNLR %>% select(ID,date,NLR_val)
FBCNLR_day1 <- semi_join(FBCNLR,total_day1, by = c("ID" = "ID", "date" = "date"))
FBCNLR_positive <- semi_join(FBCNLR,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
FBCNLR_ICU <- semi_join(FBCNLR,total_ICU, by = c("ID" = "ID", "date" = "date"))

FBCNLR$Label <- "All values"
FBCNLR_day1$Label <- "Values on admission"
FBCNLR_positive$Label <- "Values on COVID + day"
FBCNLR_ICU$Label <- "Values for ICU patients"

FBCNLR <- rbind(FBCNLR,FBCNLR_day1,FBCNLR_positive,FBCNLR_ICU)

ggplot() +
  ggtitle("FBCNLR distribution") +
  labs(subtitle="Reference range = 0.78 and 3.53") + 
  geom_boxplot(data = FBCNLR, aes(x=NLR_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=FBCNLR_ref_1,colour="red") +
  geom_vline(xintercept=FBCNLR_ref_2,colour="red") 

```

```{r}
# Reference range = 4.0-11.0 10^9/L

FBC <- read.csv(file("FBC.csv"))
FBC$Date.Booked.In = as.Date(FBC$Date.Booked.In, format="%d/%m/%Y")
FBC = FBC %>% 
  rename(
    date = Date.Booked.In,
  )

FBCWCC = FBC %>% select(ID,date,Result.WCC)
FBCWCC = FBCWCC %>% 
  rename(
    WCC = Result.WCC,
  )

FBCWCC$WCC <- (FBCWCC$WCC)^(1/3)

FBCWCC_range = range(FBCWCC$WCC, na.rm=TRUE)
FBCWCC_ref_1 = (4)^(1/3)
FBCWCC_ref_2 = (11)^(1/3)


FBCWCC$WCC <- Winsorize(FBCWCC$WCC, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

FBCWCC$WCC <- rescale(FBCWCC$WCC, to=c(0,1), from = FBCWCC_range)
FBCWCC_ref_1 = rescale(FBCWCC_ref_1, to=c(0,1), from = FBCWCC_range)
FBCWCC_ref_2 = rescale(FBCWCC_ref_2, to=c(0,1), from = FBCWCC_range)



FBCWCC = FBCWCC %>% select(ID,date,WCC)
FBCWCC_day1 <- semi_join(FBCWCC,total_day1, by = c("ID" = "ID", "date" = "date"))
FBCWCC_positive <- semi_join(FBCWCC,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
FBCWCC_ICU <- semi_join(FBCWCC,total_ICU, by = c("ID" = "ID", "date" = "date"))

FBCWCC$Label <- "All values"
FBCWCC_day1$Label <- "Values on admission"
FBCWCC_positive$Label <- "Values on COVID + day"
FBCWCC_ICU$Label <- "Values for ICU patients"

FBCWCC <- rbind(FBCWCC,FBCWCC_day1,FBCWCC_positive,FBCWCC_ICU)

ggplot() +
  ggtitle("FBCWCC distribution") +
  labs(subtitle="Reference range = 4.0-11.0 10^9/L") + 
  geom_boxplot(data = FBCWCC, aes(x=WCC, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=FBCWCC_ref_1,colour="red") +
  geom_vline(xintercept=FBCWCC_ref_2,colour="red") 

```

```{r}
# Reference range = >/= 48 mmol/mol probable diabetes, 42-48 mmol/mol increased risk

HBA1c <- read.csv(file("HBA1c.csv"))
HBA1c$Date.Booked.In = as.Date(HBA1c$Date.Booked.In, format="%d/%m/%Y")
HBA1c = HBA1c %>% 
  rename(
    date = Date.Booked.In,
  )
HBA1c = HBA1c %>%
  rename(
    HBA1c_val = Numeric.Result
  )

HBA1c$HBA1c_val <- (HBA1c$HBA1c_val)^(1/3)

HBA1c_range = range(HBA1c$HBA1c_val, na.rm=TRUE)
HBA1c_ref_1 = (42)^(1/3)
HBA1c_ref_2 = (48)^(1/3)


HBA1c$HBA1c_val <- Winsorize(HBA1c$HBA1c_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

HBA1c$HBA1c_val <- rescale(HBA1c$HBA1c_val, to=c(0,1), from = HBA1c_range)
HBA1c_ref_1 = rescale(HBA1c_ref_1, to=c(0,1), from = HBA1c_range)
HBA1c_ref_2 = rescale(HBA1c_ref_2, to=c(0,1), from = HBA1c_range)



HBA1c = HBA1c %>% select(ID,date,HBA1c_val)
HBA1c_day1 <- semi_join(HBA1c,total_day1, by = c("ID" = "ID", "date" = "date"))
HBA1c_positive <- semi_join(HBA1c,total_positiveDay, by = c("ID" = "ID", "date" = "date"))


HBA1c$Label <- "All values"
HBA1c_day1$Label <- "Values on admission"
HBA1c_positive$Label <- "Values on COVID + day"

HBA1c <- rbind(HBA1c,HBA1c_day1,HBA1c_positive)

ggplot() +
  ggtitle("HBA1c distribution") +
  labs(subtitle="Reference range = >/= 48 mmol/mol probable diabetes, 42-48 mmol/mol increased risk") + 
  geom_boxplot(data = HBA1c, aes(x=HBA1c_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=HBA1c_ref_1,colour="red") +
  geom_vline(xintercept=HBA1c_ref_2,colour="red") 

```

```{r}
# Reference range = 7.35-7.45

poctpH <- read.csv(file("poctpH.csv"))
#Format date
poctpH$Date.of.Specimen = as.Date(poctpH$Date...Time.of.Specimen, format="%d/%m/%Y")
poctpH = poctpH %>% 
  rename(
    date = Date...Time.of.Specimen,
  )
poctpH$date = as.Date(poctpH$date, format="%d/%m/%Y")
poctpH = poctpH %>% 
  rename(
    time = Time.of.Specimen,
  )
poctpH = poctpH %>% 
  rename(
    poctpH_val = Numeric.Result,
  )
#Combine date and time
poctpH$dateTime = as.POSIXct(paste(poctpH$date, poctpH$time), format="%Y-%m-%d %H:%M:%S")


poctpH_range = range(poctpH$poctpH_val, na.rm=TRUE)
poctpH_ref_1 = (7.35)
poctpH_ref_2 = (7.45)

poctpH$poctpH_val <- Winsorize(poctpH$poctpH_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

poctpH$poctpH_val <- rescale(poctpH$poctpH_val, to=c(0,1), from = poctpH_range)
poctpH_ref_1 = rescale(poctpH_ref_1, to=c(0,1), from = poctpH_range)
poctpH_ref_2 = rescale(poctpH_ref_2, to=c(0,1), from = poctpH_range)



poctpH = poctpH %>% select(ID,date,poctpH_val)
poctpH_day1 <- semi_join(poctpH,total_day1, by = c("ID" = "ID", "date" = "date"))
poctpH_positive <- semi_join(poctpH,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
poctpH_ICU <- semi_join(poctpH,total_ICU, by = c("ID" = "ID", "date" = "date"))

poctpH$Label <- "All values"
poctpH_day1$Label <- "Values on admission"
poctpH_positive$Label <- "Values on COVID + day"
poctpH_ICU$Label <- "Values for ICU patients"

poctpH <- rbind(poctpH,poctpH_day1,poctpH_positive,poctpH_ICU)

ggplot() +
  ggtitle("poctpH distribution") +
  labs(subtitle="Reference range = 7.35-7.45") + 
  geom_boxplot(data = poctpH, aes(x=poctpH_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=poctpH_ref_1,colour="red") +
  geom_vline(xintercept=poctpH_ref_2,colour="red") 

```

```{r}
# Reference range = 0.5-2.2 mmol/L

poctLAC <- read.csv(file("poctLAC.csv"))
#Format date
poctLAC$Date.of.Specimen = as.Date(poctLAC$Date.of.Specimen, format="%d/%m/%Y")
poctLAC = poctLAC %>% 
  rename(
    date = Date.of.Specimen,
  )
poctLAC = poctLAC %>% 
  rename(
    time = Time.of.Specimen,
  )
poctLAC = poctLAC %>%
  rename(
    poctLAC_val = Numeric.Result
  )
#Combine date and time
poctLAC$dateTime = as.POSIXct(paste(poctLAC$date, poctLAC$time), format="%Y-%m-%d %H:%M:%S")

poctLAC$poctLAC_val <- log10(poctLAC$poctLAC_val)

poctLAC_range = range(poctLAC$poctLAC_val, na.rm=TRUE)
poctLAC_ref_1 = log10(0.5)
poctLAC_ref_2 = log10(2.2)


poctLAC$poctLAC_val <- Winsorize(poctLAC$poctLAC_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

poctLAC$poctLAC_val <- rescale(poctLAC$poctLAC_val, to=c(0,1), from = poctLAC_range)
poctLAC_ref_1 = rescale(poctLAC_ref_1, to=c(0,1), from = poctLAC_range)
poctLAC_ref_2 = rescale(poctLAC_ref_2, to=c(0,1), from = poctLAC_range)



poctLAC = poctLAC %>% select(ID,date,poctLAC_val)
poctLAC_day1 <- semi_join(poctLAC,total_day1, by = c("ID" = "ID", "date" = "date"))
poctLAC_positive <- semi_join(poctLAC,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
poctLAC_ICU <- semi_join(poctLAC,total_ICU, by = c("ID" = "ID", "date" = "date"))

poctLAC$Label <- "All values"
poctLAC_day1$Label <- "Values on admission"
poctLAC_positive$Label <- "Values on COVID + day"
poctLAC_ICU$Label <- "Values for ICU patients"

poctLAC <- rbind(poctLAC,poctLAC_day1,poctLAC_positive, poctLAC_ICU)

ggplot() +
  ggtitle("poctLAC distribution") +
  labs(subtitle="Reference range = 0.5-2.2 mmol/L") + 
  geom_boxplot(data = poctLAC, aes(x=poctLAC_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=poctLAC_ref_1,colour="red") +
  geom_vline(xintercept=poctLAC_ref_2,colour="red") 

```

```{r}
# Reference range = 240-480 IU/L

LDH <- read.csv(file("LDH.csv"))
LDH$Date.Booked.In = as.Date(LDH$Date.Booked.In, format="%d/%m/%Y")
LDH = LDH %>% 
  rename(
    date = Date.Booked.In,
  )
LDH = LDH %>%
  rename(
    LDH_val = Numeric.Result
  )

LDH$LDH_val <- log10(LDH$LDH_val)

LDH_range = range(LDH$LDH_val, na.rm=TRUE)
LDH_ref_1 = log10(240)
LDH_ref_2 = log10(480)


LDH$LDH_val <- Winsorize(LDH$LDH_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

LDH$LDH_val <- rescale(LDH$LDH_val, to=c(0,1), from = LDH_range)
LDH_ref_1 = rescale(LDH_ref_1, to=c(0,1), from = LDH_range)
LDH_ref_2 = rescale(LDH_ref_2, to=c(0,1), from = LDH_range)



LDH = LDH %>% select(ID,date,LDH_val)
LDH_day1 <- semi_join(LDH,total_day1, by = c("ID" = "ID", "date" = "date"))
LDH_positive <- semi_join(LDH,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
LDH_ICU <- semi_join(LDH,total_ICU, by = c("ID" = "ID", "date" = "date"))

LDH$Label <- "All values"
LDH_day1$Label <- "Values on admission"
LDH_positive$Label <- "Values on COVID + day"
LDH_ICU$Label <- "Values for ICU patients"

LDH <- rbind(LDH,LDH_day1,LDH_positive, LDH_ICU)

ggplot() +
  ggtitle("LDH distribution") +
  labs(subtitle="Reference range = 240-480 IU/L") + 
  geom_boxplot(data = LDH, aes(x=LDH_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=LDH_ref_1,colour="red") +
  geom_vline(xintercept=LDH_ref_2,colour="red") 


```

```{r}
# Reference range = Normal range: <0.05ng/mL, <0.50ng/mL low risk of severe sepsis, >2.00ng/mL high risk severe sepsis

PCT <- read.csv(file("PCT.csv"))
PCT$Date.Booked.In = as.Date(PCT$Date.Booked.In, format="%d/%m/%Y")
PCT = PCT %>% 
  rename(
    date = Date.Booked.In,
  )
PCT = PCT %>%
  rename(
    PCT_val = Numeric.Result
  )


PCT$PCT_val <- log10(PCT$PCT_val)

PCT_range = range(PCT$PCT_val, na.rm=TRUE)
PCT_ref_1 = log10(0.05)
PCT_ref_2 = log10(0.5)
PCT_ref_3 = log10(2)


PCT$PCT_val <- Winsorize(PCT$PCT_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

PCT$PCT_val <- rescale(PCT$PCT_val, to=c(0,1), from = PCT_range)
PCT_ref_1 = rescale(PCT_ref_1, to=c(0,1), from = PCT_range)
PCT_ref_2 = rescale(PCT_ref_2, to=c(0,1), from = PCT_range)
PCT_ref_3 = rescale(PCT_ref_2, to=c(0,1), from = PCT_range)



PCT = PCT %>% select(ID,date,PCT_val)
PCT_day1 <- semi_join(PCT,total_day1, by = c("ID" = "ID", "date" = "date"))
PCT_positive <- semi_join(PCT,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
PCT_ICU <- semi_join(PCT,total_ICU, by = c("ID" = "ID", "date" = "date"))

PCT$Label <- "All values"
PCT_day1$Label <- "Values on admission"
PCT_positive$Label <- "Values on COVID + day"
PCT_ICU$Label <- "Values for ICU patients"

PCT <- rbind(PCT,PCT_day1,PCT_positive,PCT_ICU)

ggplot() +
  ggtitle("PCT distribution") +
  labs(subtitle="Reference range = Normal range: <0.05ng/mL, <0.50ng/mL low risk of severe sepsis, >2.00ng/mL high risk severe sepsis") + 
  geom_boxplot(data = PCT, aes(x=PCT_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=PCT_ref_1,colour="red") +
  geom_vline(xintercept=PCT_ref_2,colour="red") +
  geom_vline(xintercept=PCT_ref_3,colour="red") 

```

```{r}

# Reference range = 150-450 10^9/L

PLT <- read.csv(file("PLT.csv"))
PLT$Date.Booked.In = as.Date(PLT$Date.Booked.In, format="%d/%m/%Y")
PLT = PLT %>% 
  rename(
    date = Date.Booked.In,
  )
PLT = PLT %>%
  rename(
    PLT_val = Numeric.Result
  )

PLT$PLT_val <- sqrt(PLT$PLT_val)

PLT_range = range(PLT$PLT_val, na.rm=TRUE)
PLT_ref_1 = sqrt(150)
PLT_ref_2 = sqrt(450)


PLT$PLT_val <- Winsorize(PLT$PLT_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

PLT$PLT_val <- rescale(PLT$PLT_val, to=c(0,1), from = PLT_range)
PLT_ref_1 = rescale(PLT_ref_1, to=c(0,1), from = PLT_range)
PLT_ref_2 = rescale(PLT_ref_2, to=c(0,1), from = PLT_range)



PLT = PLT %>% select(ID,date,PLT_val)
PLT_day1 <- semi_join(PLT,total_day1, by = c("ID" = "ID", "date" = "date"))
PLT_positive <- semi_join(PLT,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
PLT_ICU <- semi_join(PLT,total_ICU, by = c("ID" = "ID", "date" = "date"))

PLT$Label <- "All values"
PLT_day1$Label <- "Values on admission"
PLT_positive$Label <- "Values on COVID + day"
PLT_ICU$Label <- "Values for ICU patients"

PLT <- rbind(PLT,PLT_day1,PLT_positive, PLT_ICU)

ggplot() +
  ggtitle("PLT distribution") +
  labs(subtitle="Reference range = 150-450 10^9/L") + 
  geom_boxplot(data = PLT, aes(x=PLT_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=PLT_ref_1,colour="red") +
  geom_vline(xintercept=PLT_ref_2,colour="red") 

```


```{r}
# Reference range = 0.5-1.7

trig <- read.csv(file("trig.csv"))
trig$Date.Booked.In = as.Date(trig$Date.Booked.In, format="%d/%m/%Y")
trig = trig %>% 
  rename(
    date = Date.Booked.In,
  )
trig = trig %>%
  rename(
    trig_val = Numeric.Result
  )

trig$trig_val <- log10(trig$trig_val)

trig_range = range(trig$trig_val, na.rm=TRUE)
trig_ref_1 = log10(0.5)
trig_ref_2 = log10(1.7)


trig$trig_val <- Winsorize(trig$trig_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

trig$trig_val <- rescale(trig$trig_val, to=c(0,1), from = trig_range)
trig_ref_1 = rescale(trig_ref_1, to=c(0,1), from = trig_range)
trig_ref_2 = rescale(trig_ref_2, to=c(0,1), from = trig_range)



trig = trig %>% select(ID,date,trig_val)
trig_day1 <- semi_join(trig,total_day1, by = c("ID" = "ID", "date" = "date"))
trig_positive <- semi_join(trig,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
trig_ICU <- semi_join(trig,total_ICU, by = c("ID" = "ID", "date" = "date"))

trig$Label <- "All values"
trig_day1$Label <- "Values on admission"
trig_positive$Label <- "Values on COVID + day"
trig_ICU$Label <- "Values for ICU patients"

trig <- rbind(trig,trig_day1,trig_positive, trig_ICU)

ggplot() +
  ggtitle("trig distribution") +
  labs(subtitle="Reference range = 0.5-1.7") + 
  geom_boxplot(data = trig, aes(x=trig_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=trig_ref_1,colour="red") +
  geom_vline(xintercept=trig_ref_2,colour="red") 

```


```{r}
# Reference range = Normal: <14ng/L, Possible MI: 14-30 ng/L, Probable MI: >30 ng/L

trop <- read.csv(file("trop.csv"))
trop$Date.Booked.In = as.Date(trop$Date.Booked.In, format="%d/%m/%Y")
trop = trop %>% 
  rename(
    date = Date.Booked.In,
  )
trop = trop %>%
  rename(
    trop_val = Numeric.Result
  )

trop$trop_val <- log10(trop$trop_val)

trop_range = range(trop$trop_val, na.rm=TRUE)
trop_ref_1 = log10(14)
trop_ref_2 = log10(30)


trop$trop_val <- Winsorize(trop$trop_val, minval = NULL, maxval = NULL,
                             probs = c(0.01, 0.99), na.rm = TRUE, type = 7)

trop$trop_val <- rescale(trop$trop_val, to=c(0,1), from = trop_range)
trop_ref_1 = rescale(trop_ref_1, to=c(0,1), from = trop_range)
trop_ref_2 = rescale(trop_ref_2, to=c(0,1), from = trop_range)



trop = trop %>% select(ID,date,trop_val)
trop_day1 <- semi_join(trop,total_day1, by = c("ID" = "ID", "date" = "date"))
trop_positive <- semi_join(trop,total_positiveDay, by = c("ID" = "ID", "date" = "date"))
trop_ICU <- semi_join(trop,total_ICU, by = c("ID" = "ID", "date" = "date"))

trop$Label <- "All values"
trop_day1$Label <- "Values on admission"
trop_positive$Label <- "Values on COVID + day"
trop_ICU$Label <- "Values for ICU patients"

trop <- rbind(trop,trop_day1,trop_positive, trop_ICU)

ggplot() +
  ggtitle("trop distribution") +
  labs(subtitle="Reference range = Normal: <14ng/L, Possible MI: 14-30 ng/L, Probable MI: >30 ng/L") + 
  geom_boxplot(data = trop, aes(x=trop_val, y=Label)) + 
  coord_flip() +
  geom_vline(xintercept=trop_ref_1,colour="red") +
  geom_vline(xintercept=trop_ref_2,colour="red") 
```

